### 2022-10-30 writeup/paper.tex
Mostly finished bibliography, and finished outline of paper

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{cite,url,amsfonts}
\usepackage{algorithm}% http://ctan.org/pkg/algorithms
\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{color}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\graphicspath{{figs/}, {../figures/}}

\begin{document}
%
\title{Artistic Curve Steganography with Musical Audio As A Carrier}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{First Author\inst{1}\orcidID{0000-1111-2222-3333}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Princeton University, Princeton NJ 08544, USA 
\email{lncs@springer.com}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
15--250 words.

\keywords{Steganography, Traveling Salesperson Art, Hidden Signals}
\end{abstract}
%
%
%
\section{Introduction}

Our goals and design constraints are as follows:
\begin{enumerate}
    \item The hidden data should be audibly imperceptible (though it does not need to be statistically imperceptible)
    \item The hidden data should be robust to compression
    \item It should be possible to decode the data without any prior knowledge/keys
    \item The hidden data should be robust to frame misalignment, or it should be possible to recover a frame alignment without any prior information
\end{enumerate}

\subsection{Prior Work in Audio Steganography}

\section{Traveling Salesperson Art}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{TSPTour.png}
  \caption{Our modified pipeline for creating TSP art.  Color on the tour indicates phase along the loop.}
  \label{fig:TSPTour}
\end{figure}

Traveling Salesperson (TSP) art \cite{bosch2004continuous, kaplan2005tsp,bosch2008connecting} is an automated artistic line drawing pipeline which computes a {\em simple closed loop} to approximate a source image.  ``Simple'' in this context does not imply a lack of complexity; rather, it means that a curve does not intersect itself (see, for example, the Jordan Curve Theorem \cite{bosch2009jordan}).  To construct such a curve, a collection of dots in the plane are first placed in a ``stipple pattern'' to approximate brightness in the image (e.g. more dots concentrate in darker regions), and then they are connected in a loop via an approximate traveling salesperson (TSP) tour.  Figure~\ref{fig:TSPTour} shows an example.  We follow the TSP Art technique of \cite{kaplan2005tsp}, with a few modifications, as described below.

\subsection{Voronoi Stippling}
\label{sec:stippling}

\begin{algorithm}
  \caption{Modified Weighted Voronoi Stippling \cite{secord2002weighted}}
  \begin{algorithmic}[1]
    \Procedure{VoronoiStipple}{$G$, $N$, $b$, $\sigma$, $f$}
    \Comment{Grayscale image $G$, $N$ target points, brightness threshold $b$, Canny edge scale $\sigma$, density factor $f$}
    \State $W_{ij} \gets \min(I_{ij}, b)$
    \State $W_{ij} \gets W_{ij} - \min(W)$
    \State $W_{ij} \gets 1 - W_{ij} / \max(W)$
    \State $C \gets \text{canny}_{\sigma}(I)$ \Comment{1 if on canny edge, 0 otherwise}
    \State $W_{ij} \gets \max(W_{ij}, C_{ij})$
    \State  Sample $N$ random points $X \in \mathbb{R}^{N \times 2}$ by density according to $W$
    \For{$k = 1:10$} \Comment{Lloyd's relaxation iterations}
        \State \begin{equation}
          X_i \gets \frac{ \sum_{(i, j) \in A_i} W_{ij} * (i, j) }{\sum_{(i, j) \in A_i} W_{ij}}
        \end{equation}
        \Comment{Where $A_i$ is the Voronoi region for point $X_i$}
    \EndFor \\
    \State Remove top $N(1-f)$ points from $X$ with furthest distance to their nearest neighbors \\
    \Return $X$
    \EndProcedure
  \end{algorithmic}
  \label{alg:voronoistipple}
\end{algorithm}

%\begin{algorithm}
%  \caption{2-Opt Approximate TSP Tour \cite{johnson1997traveling}}
%  \begin{algorithmic}[1]
%    \Procedure{TSP2Opt}{$X$}
%    \Comment{$X \in \mathbb{R}^{N \times 2}$ is a 2D point cloud}
%    \State Let $T$ be a minimum spanning tree of $X$
%    \State Let $tour$ be indices into $X$ in the order that a depth-first search visits $T$, starting at an arbitrary point
%    \While{There exits a swappable $i > 1$, $j > i$}
%      \State Reverse indices in $tour$ in $[i+1, j]$
%    \EndWhile \\
%    \EndProcedure
%  \end{algorithmic}
%  \label{alg:twoopt}
%\end{algorithm}

The first step in TSP art is to generate a stipple pattern $X$ to best approximate a grayscale image $G$.  Following the authors of \cite{kaplan2005tsp}, we use Secord's technique for Voronoi stippling \cite{secord2002weighted}.  This consists taking an initial sample of points according to some density weights $W$ and then repeatedly moving them closer the weighted centroid of their Voronoi regions (an instance of Lloyd's algorithm) so that they are spread more evenly and look less ``noisy.''  Secord \cite{secord2002weighted} takes the weight $W_{ij}$ at a pixel to be inversely proportional to its brightness, using a weight of $0$ above some brigtness threshold $b$.  This leads more dots to concentrate in darker regions; however, the algorithm may fail to sample any dots along important edges between brighter regions (the authors of \cite{li2011structure} also observed this).   To ameliorate this, we run a Canny edge detector \cite{canny1986computational} on the original image and set the weight of any pixels along an edge to be 1, so that the final weights promote samples both in darker regions and along edges of any kind.  We find this is addition is particularly helpful for line drawings, including images with text (e.g. Figure~\ref{fig:GoldenSectionsFM}).  Finally, we include the option to filter out points by density to clean up the stipple before the next step.  Algorithm~\ref{alg:voronoistipple} provides more details.

\subsection{Traveling Salesperson Tours}
\label{sec:tsp}
One a stipple has been established, the next step in TSP art is to ``connect the dots'' with a closed loop that visits each stipple point exactly once.  A loop with these properties is otherwise known as a {\em Hamiltonian cycle} on a complete graph over the points, though we'll refer to this simply as a ``tour.''  A well known objective function for a tour that doesn't ``jump too much'' is the total distance traveled, or the sum of all edge lengths, and a tour that achieves the optimum is known as a {\em traveling salesperson (TSP) tour}.  Since the TSP problem is NP-hard, the authors of  \cite{kaplan2005tsp} use the Concorde TSP solver \cite{applegate2001concorde} for an approximate solution. We opt for a simpler, technique that first creates a 2-approximation of a TSP from a depth-first traversal through the minimum spanning tree of the stipple dots, which is a already a 2-approximation of the optimal tour.  We then iteratively improve on this tour via a sequence of 2-opt relaxations \cite{johnson1997traveling}; that is, if for some $i > 1, i < j < N$ the distances between the 4 points $X_i, X_{i+1}, X_j$, and $X_{j+1}$ satisfy

\begin{figure}
  \centering
  \includegraphics[width=0.5\columnwidth]{2Opt.pdf}
  \caption{Every crossing in a tour can be removed with a 2-opt swap to yield a tour of a smaller distance, since, by the triangle inequality, $d(X_i, X_j) + d(X_{i+1}, X_{j+1}) < (a+d) + (b+c) = d(X_i, X_{i+1}) + d(X_j, X_{j+1})$.  This may introduce new crossings (shown in red), but these and other crossings will be resolved in future 2-opt swaps.}
  \label{fig:TwoOpt}
\end{figure}

\begin{equation}
  d(X_i, X_j) + d(X_{i+1}, X_{j+1}) < d(X_i, X_{i+1}) + d(X_j, X_{j+1})
\end{equation}

then it is possible to perform a swap to yield a new tour with a smaller distance.  This amounts to reversing the indices in the tour between index $i+1$ and $j$, inclusive.  We repeat this step as long as such a swap is still possible.  Though this is not guaranteed to yield an optimal TSP tour, it does produce tours which are simple; that is, every crossing is removed (Figure~\ref{fig:TwoOpt}).

\subsection{Curvature Shortening Flow}

\section{Hamiltonian Paths on Watertight Triangle Meshes}

\section{Curve Embedding in Audio}

\subsection{Overall Formulation}

Let $T = (T_1, T_2, \hdots, T_N \}$ the desired Euclidean ``target'' point sequence to embed, where each $T_i \in \mathbb{R}^d$, and let $x$ be a set of $N$ audio samples which will serve as a carrier.  The goal is to perturb the samples of $x$ so that some function of $x$ matches $T$ as closely as possible.

\subsection{Re-Parameterizing Targets for Better Fits}

\subsection{Recovering Component Scales}

\subsection{Recovering Frame Alignments}

\section{Experiments}

\subsection{Listening Experiment}

We ask questions similar to the authors of \cite{cvejic_wavelet_2002}.

\section{Discussion}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{paper}
%

\end{document}

### 2022-10-30 writeup/paper.tex
Some more work on the technique writeup

@@
 \end{enumerate}
+
+Satisfying goals 1 and 2 simultaneously is the biggest challenge of this work.
 
@@
 
-Let $T = (T_1, T_2, \hdots, T_N \}$ the desired Euclidean ``target'' point sequence to embed, where each $T_i \in \mathbb{R}^d$, and let $x$ be a set of $N$ audio samples which will serve as a carrier.
+Let $T = (T_1, T_2, \hdots, T_N \}$ the desired Euclidean target point sequence to hide, where each $T_i \in \mathbb{R}^d$, and let $x$ be a set of $N$ audio samples which will serve as a carrier.
 The goal is to perturb the samples of $x$ so that some function of $x$ matches $T$ as closely as possible.
+The function we choose is based on a ``time regularized'' version of the magnitude Short-Time Fourier Transform (STFT) which we call a {\em sliding window sum} STFT (SWS-STFT).
+As a first step, we compute a {\em non-overlapping} short-time Fourier Transform based on a chosen window length $w$:
+
+\begin{equation}
+  S_{j, k} = \sum_{n = 0}^w x_{jw + n} e^{-i 2 \pi k n / w}
+\end{equation}
+
+with a total of $N$ frames.  Then, given a second window length $\ell$, we compute the following {\em sliding window sum} $X$ of the magnitudes of $|S_{j, k}|$
+
+\begin{equation}
+  X_{j, k} = \sum_{n = 0}^{\ell-1} |S_{j+n, k}|
+\end{equation}
+
+nonnegative least squares
+
+A crucial step to keep the hidden signal imperceptible is to rescale the targets to match the dynamic range of the signals.
+Unfortunately, we lose relative scale information between the components, but we will explain how to store and recover this in Section~\ref{sec:componentscales}
+
+\subsubsection{The choice of non-overlapping windows}
+Though some other works use transforms with overlapping windows (e.g.
+\cite{hwan_sik_yun_acoustic_2010}), we find that changing different STFT bins independently can lead to STFTs that do not correspond to any real signal due to discrepancies between overlapping windows.
+An algorithm like Griffin-Lim \cite{griffin1984signal} can recover a signal whose spectrogram has a locally minimal distance to the perturbed STFT, but we find that this step introduces an unacceptable level of distortion both in the target and the carrier audio.
+This problem occurs even for real-valued transforms such as the Discrete Cosine Transform (which was used by \cite{geleta_pixinwav_2021}).
+We sidestep this problem completely by using non-overlapping windows as in \cite{xiaoxiao_dong_data_2004}.
+
+The main downside of non-overlapping windows is that they lead to fewer STFT frames.
+For instance, for a 30 second audio clip at 44100hz using a window length of 1024, we are limited to about 1292 frames, which is half of what we would get using an overlapping STFT with a hop length of 512.
+However, a quick thought experiment shows that this is still a reasonable rate.
+Suppose that we use a sliding window length $\ell=16$, for a total of 1277 carrier samples.
+Suppose also that the precision of our embedding of a 2D plane curve is roughly on par with an 8 bit per coordinate quantization in a more traditional binary encoding scheme.
+Then the total number of bits transmitted over 30 seconds is $1277 \times 8 \times 2$, or about 681 bits/second.
+This number jumps to about 1022 bits/second for a 3D curve.
+These numbers are on part with other recent techniques that are designed to be robust to noise (e.g.
+900 bits/second in the OFDM technique of \cite{eichelberger_receiving_2019}).
 
@@
 
-\subsection{Recovering Component Scales}
+In general, the SWS-STFT sequence $X$ will not have the same number of samples as the target $T$.  If we stick to scenarios where $T$ has more samples, we can index $X$ by a default function
+
+Our use of the Viterbi algorithm for re-parameterizing geometric sequences is related to the technique for corpus-based concatenative synthesis presented by the authors of \cite{schwarz2007corpus}.
+
+As a rule of thumb, we find that having a target curve with about 1.5-2x as many samples as there are SWS-STFT frames gives enough wiggle room for the Viterbi algorithm.
+Therefore, in our experiments in Section~\ref{sec:experiments}, we will generate TSP and Hamiltonian sequences with 2000 samples for our 1200-1300 SWS-STFT frames
+
+\subsection{Storing Component Scales in Phase}
+\label{sec:componentscales}
+
+We use the technique presented by the authors of \cite{xiaoxiao_dong_data_2004} to recover the scales of each component.
 
@@
 \section{Experiments}
+\label{sec:experiments}
 

### 2022-10-30 writeup/paper.tex
Wrote down the objective function

@@
 %
-\title{Artistic Curve Steganography with Musical Audio As A Carrier}
+\title{Artistic Curve Steganography Carried by Musical Audio}
 %
@@
     \item The hidden data should be audibly imperceptible (though it does not need to be statistically imperceptible)
-    \item The hidden data should be robust to compression
+    \item The hidden data should be faithfully preserved and {\em robust to compression}
     \item It should be possible to decode the data without any prior knowledge/keys
@@
 The function we choose is based on a ``time regularized'' version of the magnitude Short-Time Fourier Transform (STFT) which we call a {\em sliding window sum} STFT (SWS-STFT).
-As a first step, we compute a {\em non-overlapping} short-time Fourier Transform based on a chosen window length $w$:
+As a first step, we compute a {\em non-overlapping} short-time Fourier Transform $S$ based on a chosen window length $w$ with a total of $N$ frames:
 
 \begin{equation}
-  S_{j, k} = \sum_{n = 0}^w x_{jw + n} e^{-i 2 \pi k n / w}
+  S_{j, k} = \left( \sum_{n = 0}^w x_{jw + n} e^{-i 2 \pi k n / w} \right) = M_{j, k} e^{i P_{j, k}}
 \end{equation}
 
-with a total of $N$ frames.  Then, given a second window length $\ell$, we compute the following {\em sliding window sum} $X$ of the magnitudes of $|S_{j, k}|$
+and we factor $S$ it into its magnitude and phase components $M$ and $P$, respectively.
+Then, given a second window length $\ell$, we compute the following {\em sliding window sum} $X$ of the magnitudes of $S$
 
 \begin{equation}
-  X_{j, k} = \sum_{n = 0}^{\ell-1} |S_{j+n, k}|
+  X_{j, k} = \sum_{n = 0}^{\ell-1} M_{j+n, k}
 \end{equation}
 
-nonnegative least squares
+In this way, $X$ has $N-\ell+1$ samples.
+Let's assume momentarily that $T$ has exactly this many samples; we will address the general case in Section~\ref{sec:reparam}.
+We also chose to hide each coordinate in a single frequency bin $k$; we'll index each dimension $i$'s frequency bin as $k_i$.
+Then our goal is to find a perturbed version of the magnitudes, $\hat{M}$.
+We minimize the following objective function one coordinate dimension $k = 1, ...
+d$ at a time:
+
+\begin{equation}
+  \label{eq:objfn}
+  f_k(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( \left( \sum_{n = 0}^{\ell-1} M_{j+n, k} \right) - T_{j, k} \right)^2 + \lambda \sum_{j=1}^N \left( M_{j, k} - \hat{M}_{j, k} \right)^2
+\end{equation}
+
+subject to .
+This can be formulated as a sparse nonnegative least squares problem.
+Though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity, the linear operator and its adjoint can be implemented with a number of operations proportional to $N$ only, and independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}; that is, if we let
+
+\subsubsection{Target Rescaling}
 
@@
 \subsubsection{The choice of non-overlapping windows}
-Though some other works use transforms with overlapping windows (e.g.
-\cite{hwan_sik_yun_acoustic_2010}), we find that changing different STFT bins independently can lead to STFTs that do not correspond to any real signal due to discrepancies between overlapping windows.
+Though some other works use transforms with overlapping windows (\cite{hwan_sik_yun_acoustic_2010,geleta_pixinwav_2021}), we find that changing different STFT bins independently can lead to STFTs that do not correspond to any real signal due to discrepancies between overlapping windows.
 An algorithm like Griffin-Lim \cite{griffin1984signal} can recover a signal whose spectrogram has a locally minimal distance to the perturbed STFT, but we find that this step introduces an unacceptable level of distortion both in the target and the carrier audio.
@@
 For instance, for a 30 second audio clip at 44100hz using a window length of 1024, we are limited to about 1292 frames, which is half of what we would get using an overlapping STFT with a hop length of 512.
-However, a quick thought experiment shows that this is still a reasonable rate.
+However, a quick thought experiment shows that this is still a reasonable data rate.
 Suppose that we use a sliding window length $\ell=16$, for a total of 1277 carrier samples.
-Suppose also that the precision of our embedding of a 2D plane curve is roughly on par with an 8 bit per coordinate quantization in a more traditional binary encoding scheme.
+Suppose also that the precision of our embedding of a 2D plane curve is roughly on par with an 8 bit per coordinate quantization in a more conventional binary encoding scheme.
 Then the total number of bits transmitted over 30 seconds is $1277 \times 8 \times 2$, or about 681 bits/second.
@@
 900 bits/second in the OFDM technique of \cite{eichelberger_receiving_2019}).
+Furthermore, our equivalent of a ``bit error'' is additive coordinate noise,and the target can still be visible with some amount of such noise.
 
 \subsection{Re-Parameterizing Targets for Better Fits}
+\label{sec:reparam}
 

### 2022-10-30 src/stego.py
Adding figure on length distortion

@@ -415,7 +415,7 @@ class StegoSolver:
                 b = np.mean(signal-a*self.targets[i][path])
                 self.targets[i] = a*self.targets[i] + b
                 diff += np.sum((target[path]-signal)**2)
-            print("Diff Before Viterbi", diff)
+            #print("Diff Before Viterbi", diff)
         if do_viterbi:
             csm = np.zeros((M, N))
             for target, signal in zip(self.targets, signals):
@@ -429,7 +429,7 @@ class StegoSolver:
                     b = np.mean(signal-a*self.targets[i][path])
                     self.targets[i] = a*self.targets[i] + b
                     diff += np.sum((target[path]-signal)**2)
-                print("Diff After Viterbi", diff)
+                #print("Diff After Viterbi", diff)
         if len(path) > 0:
             self.targets = [t[path] for t in self.targets]
         self.path = path

### 2022-10-30 writeup/paper.tex
Adding figure on length distortion
Added batch script to create turk samples

@@
 Satisfying goals 1 and 2 simultaneously is the biggest challenge of this work.
+
+Pipeline is simple enough that we have very good intuition for how it's working, and we validate its performance in Section~\ref{sec:experiments}.
 
@@
 In this way, $X$ has $N-\ell+1$ samples.
-Let's assume momentarily that $T$ has exactly this many samples; we will address the general case in Section~\ref{sec:reparam}.
+Let's assume momentarily that $T$ has exactly this many samples; we will address the case where $len(T) > N-\ell+1$ in Section~\ref{sec:reparam}.
 We also chose to hide each coordinate in a single frequency bin $k$; we'll index each dimension $i$'s frequency bin as $k_i$.
@@
 This can be formulated as a sparse nonnegative least squares problem.
-Though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity, the linear operator and its adjoint can be implemented with a number of operations proportional to $N$ only, and independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}; that is, if we let
+Though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function, the linear operator and its adjoint can be implemented with a number of operations proportional to $N$ only, and independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}; that is, if we let
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{OptimalShift.pdf}
+  \caption{Curve length can be used as a proxy for distortion.}
+  \label{fig:TSPTour}
+\end{figure}
+
 \section{Experiments}
@@
 
-We ask questions similar to the authors of \cite{cvejic_wavelet_2002}.
+We can actually get higher SNRs using frequencies that are more audible
+
+We ask questions similar to the authors of \cite{bassia2001robust}.
 

### 2022-10-30 data/turksamples.py

@@ -1,0 +1,114 @@
+import numpy as np
+import scipy.io as sio
+from scipy.io import wavfile
+import librosa
+import os
+import subprocess
+import sys
+import glob
+import time
+import json
+
+if __name__ == '__main__':
+    ## Step 1: Establish repository path and import source files
+    repo_path = sys.argv[0]
+    repo_path = repo_path.split("turksamples.py")[0] + ".."
+    sys.path.append(repo_path + "/src")
+    from spectrogramtools import *
+    from stego import *
+    from swpowerstego import *
+    from curvature import *
+    
+    ## Step 2: Load audio
+    audio_idx = int(sys.argv[1])
+    audio_files = sorted(glob.glob("{}/data/GTzan/*/*.au".format(repo_path)))
+    n_audiofiles = len(audio_files)
+    audio_filename = audio_files[audio_idx]
+    x, sr = librosa.load(audio_filename, sr=44100)
+    win_length = 1024
+    freqs = [1, 2]
+
+    ## Step 3: Find associated TSP paths in shuffled list
+    np.random.seed(0)
+    tsp_paths = glob.glob("{}/data/caltech-101/*/*.mat".format(repo_path))
+    tsp_paths = sorted(tsp_paths)
+    tsp_paths = [tsp_paths[i] for i in np.random.permutation(len(tsp_paths))]
+    tsp_path = tsp_paths[audio_idx]
+
+    ## Step 4: Do embedding and create audio clip
+    X = sio.loadmat(tsp_path)["X"]
+    s = get_arclen(get_curv_vectors(X, 0, 1, loop=True)[1])
+    X = arclen_resample(X, s, X.shape[0])
+    sigma = 1
+    X = get_curv_vectors(X, 0, sigma, loop=True)[0]
+
+    # First store length of normalized TSP path
+    win = 16
+    do_viterbi=True
+    fit_lam = [0.1, 1, 10, np.inf][audio_idx%4]
+    distortion = np.inf
+    snr = np.inf
+    length = np.inf
+    turk_prefix = "{}/data/turksamples/{}".format(repo_path, audio_idx)
+
+    y = np.array(x)
+    if np.isfinite(fit_lam):
+        q = -1
+        sp = STFTPowerDisjoint(x, X, win_length, freqs, freqs, win, fit_lam, q, do_viterbi=do_viterbi)
+        tic = time.time()
+        sp.solve()
[…]

### 2022-10-30 data/shiftexperiment.py
Adding shift experiments batch script

@@ -1,0 +1,115 @@
+import numpy as np
+import scipy.io as sio
+from scipy.io import wavfile
+import librosa
+import os
+import subprocess
+import sys
+import glob
+import time
+import json
+
+if __name__ == '__main__':
+    ## Step 1: Establish repository path and import source files
+    repo_path = sys.argv[0]
+    repo_path = repo_path.split("shiftexperiment.py")[0] + ".."
+    sys.path.append(repo_path + "/src")
+    from spectrogramtools import *
+    from stego import *
+    from swpowerstego import *
+    from curvature import *
+    
+    ## Step 2: Load audio
+    audio_idx = int(sys.argv[1])
+    audio_files = sorted(glob.glob("{}/data/GTzan/*/*.au".format(repo_path)))
+    n_audiofiles = len(audio_files)
+    audio_filename = audio_files[audio_idx]
+    x, sr = librosa.load(audio_filename, sr=44100)
+    win_length = 1024
+    freqs = [1, 2]
+
+    ## Step 3: Find associated TSP paths in shuffled list
+    np.random.seed(0)
+    tsp_paths = glob.glob("{}/data/caltech-101/*/*.mat".format(repo_path))
+    tsp_paths = sorted(tsp_paths)
+    tsp_paths = [tsp_paths[i] for i in np.random.permutation(len(tsp_paths))]
+    K = len(tsp_paths)//n_audiofiles
+    tsp_paths = tsp_paths[K*audio_idx:K*(audio_idx+1)]
+
+    win = 16
+    do_viterbi=True
+    q = -1
+    n_trials = 4
+
+    res = {'fit_lam':[], 'distortion':[], 'snr':[], 'length':[], 'tsp_path':[], 'audio_filename':[], 'gt_shift':[], 'recovered_shift':[], 'recovered_distortion':[]}
+    for tsp_path in tsp_paths:
+        ## Step 4: Do embedding and create audio clip
+        X = sio.loadmat(tsp_path)["X"]
+        s = get_arclen(get_curv_vectors(X, 0, 1, loop=True)[1])
+        X = arclen_resample(X, s, X.shape[0])
+        sigma = 1
+        X = get_curv_vectors(X, 0, sigma, loop=True)[0]
+
+        for fit_lam in [0.1, 1, 10]:
+            sp = STFTPowerDisjoint(x, X, win_length, freqs, freqs, win, fit_lam, q, do_viterbi=do_viterbi)
+            tic = time.time()
[…]

### 2022-10-30 writeup/paper.tex
Adding Turk results

@@
 
-\subsection{Listening Experiment}
+Below we assess the performance of our system on an extensive set of tests
+
+Show caltech-101 and meshseg examples
+
+\subsection{Quantitative Metrics}
+
+\subsection{Subjective Listening Experiment}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\columnwidth]{Turk.pdf}
+  \caption{Results of the listening experiment on the Amazon Mechanical Turk}
+  \label{fig:TurkResults}
+\end{figure}
 
@@
 We ask questions similar to the authors of \cite{bassia2001robust}.
+
+46 unique Turkers, 21 of whom participated in at least 40 rankings.
+
+Figure~\ref{fig:TurkResults} shows the results.
+Mean opinion scores are correlated with $\lambda$, but there's not much of a difference between $\lambda=0.1$ and $\lambda=1$, which suggests using the former as a rule of thumb due to its lower geometric distortion.
 

### 2022-10-30 data/turksamples.py

@@ -34,6 +34,7 @@ if __name__ == '__main__':
     tsp_paths = sorted(tsp_paths)
     tsp_paths = [tsp_paths[i] for i in np.random.permutation(len(tsp_paths))]
     tsp_path = tsp_paths[audio_idx]
+    print(tsp_path)
 
     ## Step 4: Do embedding and create audio clip
     X = sio.loadmat(tsp_path)["X"]

### 2022-11-12 writeup/paper.tex
Adding some new figures on TSP curves
Adding figures to show the effects of different parameters, and improving the section introducting the objective function

@@
 \usepackage{color}
+\usepackage{hyperref}
 % Used for displaying a sample figure. If possible, figure files should
@@
 \begin{enumerate}
-    \item The hidden data should be audibly imperceptible (though it does not need to be statistically imperceptible)
-    \item The hidden data should be faithfully preserved and {\em robust to compression}
-    \item It should be possible to decode the data without any prior knowledge/keys
-    \item The hidden data should be robust to frame misalignment, or it should be possible to recover a frame alignment without any prior information
+    \item \label{goal:imperceptible} The hidden data should be audibly imperceptible
+    \item \label{goal:geomquality} The hidden data should be faithfully preserved and {\em robust to compression}
+    \item \label{goal:nokeys} It should be possible to decode the data without any prior knowledge/keys
+    \item \label{goal:misalignment} The hidden data should be robust to frame misalignment, or it should be possible to recover a frame alignment without any prior information
+    \item \label{goal:partial} It should be possible to recover the data partially from partial audio chunks; that is, we don't need to wait for the entire data stream to recover the signal
 \end{enumerate}
 
-Satisfying goals 1 and 2 simultaneously is the biggest challenge of this work.
+Goals ~\ref{goal:imperceptible} and ~\ref{goal:geomquality} are at odds with each other, and satisfying them simultaneously is the biggest challenge of this work.
 
@@
   \centering
-  \includegraphics[width=\columnwidth]{TSPTour.png}
+  \includegraphics[width=\columnwidth]{TSPTour.pdf}
   \caption{Our modified pipeline for creating TSP art.  Color on the tour indicates phase along the loop.}
@@
 ``Simple'' in this context does not imply a lack of complexity; rather, it means that a curve does not intersect itself (see, for example, the Jordan Curve Theorem \cite{bosch2009jordan}).
-To construct such a curve, a collection of dots in the plane are first placed in a ``stipple pattern'' to approximate brightness in the image (e.g.
-more dots concentrate in darker regions), and then they are connected in a loop via an approximate traveling salesperson (TSP) tour.
+To construct such a curve, we first place a collection of dots in the plane in a ``stipple pattern'' to approximate brightness in the image (e.g.
+more dots concentrate in darker regions), and then connect them in a loop via an approximate traveling salesperson (TSP) tour.
 Figure~\ref{fig:TSPTour} shows an example.
@@
 To ameliorate this, we run a Canny edge detector \cite{canny1986computational} on the original image and set the weight of any pixels along an edge to be 1, so that the final weights promote samples both in darker regions and along edges of any kind.
-We find this is addition is particularly helpful for line drawings, including images with text (e.g.
-Figure~\ref{fig:GoldenSectionsFM}).
+This addition is particularly helpful for line drawings, including images with text (e.g.
+Figure~\ref{fig:caltech101examples}).
 Finally, we include the option to filter out points by density to clean up the stipple before the next step.
@@
 \label{sec:tsp}
-One a stipple has been established, the next step in TSP art is to ``connect the dots'' with a closed loop that visits each stipple point exactly once.
-A loop with these properties is otherwise known as a {\em Hamiltonian cycle} on a complete graph over the points, though we'll refer to this simply as a ``tour.''  A well known objective function for a tour that doesn't ``jump too much'' is the total distance traveled, or the sum of all edge lengths, and a tour that achieves the optimum is known as a {\em traveling salesperson (TSP) tour}.
+Once a stipple has been established, the next step in TSP art is to ``connect the dots'' with a closed loop that visits each stipple point exactly once, referred to as a ``tour''\footnote{A loop with these properties is otherwise known as a {\em Hamiltonian cycle} on a complete graph over the points}.
+A well known objective function for a tour that doesn't ``jump too much'' is the total distance traveled, or the sum of all edge lengths, and a tour that achieves the optimum is known as a {\em traveling salesperson (TSP) tour}.
 Since the TSP problem is NP-hard, the authors of  \cite{kaplan2005tsp} use the Concorde TSP solver \cite{applegate2001concorde} for an approximate solution.
-We opt for a simpler, technique that first creates a 2-approximation of a TSP from a depth-first traversal through the minimum spanning tree of the stipple dots, which is a already a 2-approximation of the optimal tour.
+We opt for a simpler technique that first creates a 2-approximation of a TSP from a depth-first traversal through the minimum spanning tree of the stipple dots, which is a already a 2-approximation of the optimal tour.
 We then iteratively improve on this tour via a sequence of 2-opt relaxations \cite{johnson1997traveling}; that is, if for some $i > 1, i < j < N$ the distances between the 4 points $X_i, X_{i+1}, X_j$, and $X_{j+1}$ satisfy
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{CurvatureShortening.png}
+  \caption{Anticipating that mp3 compression will introduce noise to our embedded curves, we pre-smooth them before hiding them using one application of curvature-shortening flow, which smooths the curves without introducing any crossings.
+We find $\sigma=1$ to be a good tradeoff between smoothness and detail.}
+  \label{fig:CurvatureShortening}
+\end{figure}
+
+Since mp3 compression introduces noise into our embedded curves, we smooth them before embedding to improve visual quality.
+To this end, we apply a numerical version of curvature shortening flow described by Mokhtarian and Mackworth \cite{mokhtarian1992theory} which applies to piecewise linear curves (like our TSP tours).
+The technique works by numerically by convolving coordinates of each curve with smoothed versions of Gaussians and their derivatives.
+In particular, let
+\begin{equation}
+  g_{\sigma}[j] = c_1 e^{-j^2 / (2 \sigma^2)}, 
+  g'_{\sigma}[j] = - c_2 \frac{j}{\sigma^2} e^{-j^2 / (2 \sigma^2)}
+\end{equation}
+
+where $c_1$ and $c_2$ are appropriate normalization constants.  Then we can estimate the arc length of a sampled curve $\gamma[j]$ with the rectangular integral of a smoothed velocity estimate:
+
+\begin{equation}
+  \label{eq:arclen}
+  s_{\sigma}[j] = \sum_{k=1}^j |(\gamma * g'_{\sigma})[k]|
+\end{equation}
+
+To approximately smooth a curve via one step of curvature-shortening flow, Mokhtarian and Mackworth \cite{mokhtarian1992theory} show that it suffices to first re-parameterize by the arc length $s_{\sigma}$ in Equation~\ref{eq:arclen}, and then to smooth the curve by convolving with $g_{\sigma}$.
+The beauty of convolving with Gaussians as such is that $\gamma$ does not even have to be differentiable, so this works on our piecewise linear TSP tours.
+Furthermore, by the Gage-Hamilton-Grayson theorem, simple curves that undergo curvature shortening flow {\em remain simple} and eventually become convex, shrinking to a point under repeated applications of the flow.
+Figure~\ref{fig:CurvatureShortening} shows an example of one application of curvature shortening flow for different $\sigma$ values.
+
 \section{Hamiltonian Paths on Watertight Triangle Meshes}
+\label{sec:hamiltonian}
 
@@
 
-\subsection{Overall Formulation}
+We now introduce our new algorithm for hiding artistic space curves, such as 2D TSP paths (Section~\ref{sec:tsp}) and 3D Hamiltonian paths (Section~\ref{sec:hamiltonian}), in audio.
 
-Let $T = (T_1, T_2, \hdots, T_N \}$ the desired Euclidean target point sequence to hide, where each $T_i \in \mathbb{R}^d$, and let $x$ be a set of $N$ audio samples which will serve as a carrier.
+\subsection{Formulation of Least Squares Problem}
+
+Let $T = (T_1, T_2, \hdots, T_N \}$ the desired Euclidean target point sequence to hide, where each $T_i \in \mathbb{R}^d$, and $T_i[m]$ refers to the $m^{\text{th}}$ coordinate of $T_i$, and let $x$ be a set of audio samples which will serve as a carrier.
 The goal is to perturb the samples of $x$ so that some function of $x$ matches $T$ as closely as possible.
 The function we choose is based on a ``time regularized'' version of the magnitude Short-Time Fourier Transform (STFT) which we call a {\em sliding window sum} STFT (SWS-STFT).
-As a first step, we compute a {\em non-overlapping} short-time Fourier Transform $S$ based on a chosen window length $w$ with a total of $N$ frames:
+As a first step, we compute a {\em non-overlapping} STFT $S$ based on a chosen window length $w$ with a total of $N$ frames:
 
 \begin{equation}
-  S_{j, k} = \left( \sum_{n = 0}^w x_{jw + n} e^{-i 2 \pi k n / w} \right) = M_{j, k} e^{i P_{j, k}}
+  S_{k, j} = \sum_{n = 0}^w x_{jw + n} \left(e^{-i 2 \pi k n / w} \right) = M_{k, j} \left( e^{i P_{k, j}} \right)
 \end{equation}
@@
 and we factor $S$ it into its magnitude and phase components $M$ and $P$, respectively.
-Then, given a second window length $\ell$, we compute the following {\em sliding window sum} $X$ of the magnitudes of $S$
+Then, given a second window length $\ell$, we define the following {\em sliding window sum} function, which we apply to each row $k$ of the magnitudes of $S$ that we wish to perturb to obtain the SWS-STFT
 
 \begin{equation}
-  X_{j, k} = \sum_{n = 0}^{\ell-1} M_{j+n, k}
+  \text{SWS}_{\ell}\left({M_k}\right)_j = \sum_{n = 0}^{\ell-1} M_{k, j+n}
 \end{equation}
 
-In this way, $X$ has $N-\ell+1$ samples.
+The effect of $\ell$ is to smooth out the noisy time series at each row $k$ of the magnitude spectrogram so that the rows in the SW-STFT match smoother transitions in the target curves.
+The resulting time series $\text{SWS}_{\ell}\left({M_k}\right)$ has $N-\ell+1$ samples.
 Let's assume momentarily that $T$ has exactly this many samples; we will address the case where $len(T) > N-\ell+1$ in Section~\ref{sec:reparam}.
-We also chose to hide each coordinate in a single frequency bin $k$; we'll index each dimension $i$'s frequency bin as $k_i$.
-Then our goal is to find a perturbed version of the magnitudes, $\hat{M}$.
-We minimize the following objective function one coordinate dimension $k = 1, ...
+We seek a perturbed version of the magnitudes, $\hat{M}$ so that each coordinate $i$ is hidden in a single frequency index $k_i$ of $\hat{M}$.
+To that end, we minimize the following objective function, one coordinate dimension $i = 1, ...
 d$ at a time:
@@
   \label{eq:objfn}
-  f_k(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( \left( \sum_{n = 0}^{\ell-1} M_{j+n, k} \right) - T_{j, k} \right)^2 + \lambda \sum_{j=1}^N \left( M_{j, k} - \hat{M}_{j, k} \right)^2
+  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( \left( \sum_{n = 0}^{\ell-1} \hat{M}_{k_i, j+n} \right) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k, j} - \hat{M}_{k, j} \right)^2
 \end{equation}
 
-subject to .
-This can be formulated as a sparse nonnegative least squares problem.
-Though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function, the linear operator and its adjoint can be implemented with a number of operations proportional to $N$ only, and independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}; that is, if we let
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{WindowEffect.pdf}
+  \caption{A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive mp3 encoding, but an $\ell$ that's too large can over-smooth.}
+  \label{fig:WindowEffect}
+\end{figure}
 
-\subsubsection{Target Rescaling}
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{LambdaEffect.pdf}
+  \caption{A smaller $\lambda$ in Equation~\ref{eq:objfn} leads to higher geometric fidelity (Goal~\ref{goal:geomquality}), at the cost of audio quality (Goal~\ref{goal:imperceptible}), as measured by SNR.}
+  \label{fig:LambdaEffect}
+\end{figure}
 
-A crucial step to keep the hidden signal imperceptible is to rescale the targets to match the dynamic range of the signals.
-Unfortunately, we lose relative scale information between the components, but we will explain how to store and recover this in Section~\ref{sec:componentscales}
+subject to $\hat{M_{k, j}} \geq 0$.
+In other words, we want the magnitude SW-STFT of a perturbed signal to match the target coordinate as well as possible, while preserving the original audio as well as possible, according to $\lambda$.
+A greater $\lambda$ means that the signal will fit the original audio better, at the cost of a noisier curve.
+Figure~\ref{fig:LambdaEffect} shows some examples.
+
+\subsubsection{Efficient Computation}
+\label{sec:computation}
+Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem.
+Though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function, the linear operator and its adjoint can be implemented with a number of operations proportional to $N$ only, and independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}.
+
+It is also worth noting that a higher $\lambda$ in equation~\ref{eq:objfn} leads to a lower condition number\footnote{The condition number of a matrix is defined as the ratio of the largest to smallest singular values, and lower condition numbers are more numerically desireable.} of the matrix in the implied linear system, which leads to faster computation.
+But as Figure~\ref{fig:LambdaEffect} shows, it may be worth it to use smaller $\lambda$ values.
+In practice, we see it as a difference between an encoding in 30 seconds of audio that takes a few seconds for $\lambda=0.1$ versus an encoding that takes a split second for $\lambda=10$ on a CPU.
 
@@
 
-\subsection{Re-Parameterizing Targets for Better Fits}
+\subsection{Rescaling And Re-Parameterizing Targets for Better Fits}
 \label{sec:reparam}
+
+A crucial step to keep the hidden signal imperceptible is to rescale the targets to match the dynamic range of the signals.
+Unfortunately, we lose relative scale information between the components, but we will explain how to store and recover this in Section~\ref{sec:componentscales}
 
@@
 Show caltech-101 and meshseg examples
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{caltech101_samples.pdf}
+  \caption{Examples of some TSP art on the Caltech-101 dataset \cite{li_andreeto_ranzato_perona_2022}.}
+  \label{fig:caltech101examples}
+\end{figure}
 

### 2022-11-12 writeup/paper.tex
Fixing mistake in turk figure

@@
 Let's assume momentarily that $T$ has exactly this many samples; we will address the case where $len(T) > N-\ell+1$ in Section~\ref{sec:reparam}.
-We seek a perturbed version of the magnitudes, $\hat{M}$ so that each coordinate $i$ is hidden in a single frequency index $k_i$ of $\hat{M}$.
+We then seek a perturbed version of the magnitudes, $\hat{M}$ so that each coordinate $i$ is hidden in a single frequency index $k_i$ of $\hat{M}$.
 To that end, we minimize the following objective function, one coordinate dimension $i = 1, ...
@@
   \includegraphics[width=\columnwidth]{WindowEffect.pdf}
-  \caption{A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive mp3 encoding, but an $\ell$ that's too large can over-smooth.}
+  \caption{This figure shows the effect of varying $\ell$ for a fixed $\lambda=0.1$.
+A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive compression, but an $\ell$ that's too large can over-smooth.}
   \label{fig:WindowEffect}
@@
   \includegraphics[width=\columnwidth]{LambdaEffect.pdf}
-  \caption{A smaller $\lambda$ in Equation~\ref{eq:objfn} leads to higher geometric fidelity (Goal~\ref{goal:geomquality}), at the cost of audio quality (Goal~\ref{goal:imperceptible}), as measured by SNR.}
+  \caption{This figure shows the effect of varying $\lambda$ for a fixed $\ell=16$.
+A smaller $\lambda$ in Equation~\ref{eq:objfn} leads to higher geometric fidelity (Goal~\ref{goal:geomquality}), at the cost of audio quality (Goal~\ref{goal:imperceptible}), as measured by SNR.}
   \label{fig:LambdaEffect}
@@
 
-\subsubsection{Efficient Computation}
+\subsubsection{Computational Complexity}
 \label{sec:computation}
-Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem.
-Though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function, the linear operator and its adjoint can be implemented with a number of operations proportional to $N$ only, and independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}.
+Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem, and there are myriad algorithms for solving such systems efficiently via repeated evaluation of the linear system and its adjoint.
+Furthermore, though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function at each iteration, the linear operator and its adjoint can be implemented with $O(N)$ operations only, independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}.
+For example, let
+
+\begin{equation}
+  \label{eq:cumusum}
+  C_{k, j} = \sum_{i=j}^{j+\ell} \hat{M_{k, i}}
+\end{equation}
+
+then Equation~\ref{eq:objfn} can be rewritten as 
+\begin{equation}
+  \label{eq:objfncumusum}
+  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( (C_{k, j+\ell}-C_{k, j}) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k, j} - \hat{M}_{k, j} \right)^2
+\end{equation}
+
+A similar trick can be used for the adjoint operator.
 
@@
 
-The main downside of non-overlapping windows is that they lead to fewer STFT frames.
-For instance, for a 30 second audio clip at 44100hz using a window length of 1024, we are limited to about 1292 frames, which is half of what we would get using an overlapping STFT with a hop length of 512.
+Aside from window effects, the main downside of non-overlapping windows is that they lead to fewer STFT frames.
+For instance, with a 30 second audio clip at 44100hz using a window length of 1024, we are limited to about 1292 frames, which is half of what we would get using an overlapping STFT with a hop length of 512.
 However, a quick thought experiment shows that this is still a reasonable data rate.
@@
 This number jumps to about 1022 bits/second for a 3D curve.
-These numbers are on part with other recent techniques that are designed to be robust to noise (e.g.
+These numbers are on par with other recent techniques that are designed to be robust to noise (e.g.
 900 bits/second in the OFDM technique of \cite{eichelberger_receiving_2019}).
-Furthermore, our equivalent of a ``bit error'' is additive coordinate noise,and the target can still be visible with some amount of such noise.
+Furthermore, our equivalent of a ``bit error'' is additive coordinate noise, and the hidden signal degrades continuously with increased noise, rather than reaching a failure mode when a bit error is too high.
 

### 2022-11-13 writeup/paper.tex
Adding section on hamiltonian cycles

@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{HamiltonianHorse.pdf}
+  \caption{An example of the algorithm of Gopi and Epstein \cite{gopi2004single} on a horse model from the Princeton mesh segmentation benchmark \cite{Chen:2009:ABF}.}
+  \label{fig:HamiltonianHorse}
+\end{figure}
+
+In addition to 2D TSP tours on stipple patterns on planar images, we can also create artistic 3D space curves that fill out the surfaces of 3D shapes following the technique of Gopi and Epstein \cite{gopi2004single}.
+They observe that watertight triangle meshes (those with no boundary) have a dual graph in which a perfect matching exists.
+In other words, it is possible to partition the triangles into a set of adjacent pairs (second column of Figure~\ref{fig:HamiltonianHorse}).
+Adding edges between unpaired triangles leads to a set of disconnected cycles (third column of Figure~\ref{fig:HamiltonianHorse}), which can be connected by a spanning set of edges between paired triangles.
+Finally, the spanning edges can be split into bridges between the cycles disconnected cycles, joining them together into one large cycle that covers the surface of the triangle mesh.
+
 \section{Curve Embedding in Audio}
@@
 A greater $\lambda$ means that the signal will fit the original audio better, at the cost of a noisier curve.
-Figure~\ref{fig:LambdaEffect} shows some examples.
+Figure~\ref{fig:LambdaEffect} shows an example of varying $\lambda$.
 
@@
 
-A similar trick can be used for the adjoint operator.
-
-It is also worth noting that a higher $\lambda$ in equation~\ref{eq:objfn} leads to a lower condition number\footnote{The condition number of a matrix is defined as the ratio of the largest to smallest singular values, and lower condition numbers are more numerically desireable.} of the matrix in the implied linear system, which leads to faster computation.
-But as Figure~\ref{fig:LambdaEffect} shows, it may be worth it to use smaller $\lambda$ values.
+It is also worth noting that a higher $\lambda$ in equation~\ref{eq:objfn} leads to a lower condition number\footnote{The condition number of a matrix is defined as the ratio of the largest to smallest singular values, and lower condition numbers are more numerically desireable.} of the matrix in the implied linear system, which leads to faster minimization of Equation~\ref{eq:objfn}.
+But as Figure~\ref{fig:LambdaEffect} shows, it may still be worth it to use smaller $\lambda$ values.
 In practice, we see it as a difference between an encoding in 30 seconds of audio that takes a few seconds for $\lambda=0.1$ versus an encoding that takes a split second for $\lambda=10$ on a CPU.

### 2022-11-13 writeup/paper.tex
Adding mesh segmentation examples

@@
     \item \label{goal:geomquality} The hidden data should be faithfully preserved and {\em robust to compression}
-    \item \label{goal:nokeys} It should be possible to decode the data without any prior knowledge/keys
     \item \label{goal:misalignment} The hidden data should be robust to frame misalignment, or it should be possible to recover a frame alignment without any prior information
@@
 In other words, it is possible to partition the triangles into a set of adjacent pairs (second column of Figure~\ref{fig:HamiltonianHorse}).
-Adding edges between unpaired triangles leads to a set of disconnected cycles (third column of Figure~\ref{fig:HamiltonianHorse}), which can be connected by a spanning set of edges between paired triangles.
+In practice, we use the Blossom-5 algorithm \cite{kolmogorov2009blossom} to find perfect matches of the dual graph.
+Then, adding edges between unpaired triangles leads to a set of disconnected cycles (third column of Figure~\ref{fig:HamiltonianHorse}), which can be connected by a spanning set of edges between paired triangles.
 Finally, the spanning edges can be split into bridges between the cycles disconnected cycles, joining them together into one large cycle that covers the surface of the triangle mesh.
@@
 We now introduce our new algorithm for hiding artistic space curves, such as 2D TSP paths (Section~\ref{sec:tsp}) and 3D Hamiltonian paths (Section~\ref{sec:hamiltonian}), in audio.
+Before we go into the details, we first define quantitative measurements for measuring the fit to the original audio (Goal~\ref{goal:imperceptible}) and the geometric quality of the hidden curve (Goal~\ref{goal:geomquality}).
 
@@
   \centering
-  \includegraphics[width=\columnwidth]{caltech101_samples.pdf}
+  \includegraphics[width=\columnwidth]{caltech101_samples.png}
   \caption{Examples of some TSP art on the Caltech-101 dataset \cite{li_andreeto_ranzato_perona_2022}.}
@@
 
-\subsection{Quantitative Metrics}
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{MeshSegExamples.png}
+  \caption{Examples of some Hamiltonian cycles on triangle meshes from the Princeton mesh segmentation benchmark \cite{Chen:2009:ABF}.}
+  \label{fig:meshsegexamples}
+\end{figure}
+
+\subsection{Quantitative Results}
 

### 2022-11-13 writeup/paper.tex
Mostly finished writing about frame misalignments

@@
 \begin{equation}
-  S_{k, j} = \sum_{n = 0}^w x_{jw + n} \left(e^{-i 2 \pi k n / w} \right) = M_{k, j} \left( e^{i P_{k, j}} \right)
+  S_{k_i, j} = \sum_{n = 0}^w x_{jw + n} \left(e^{-i 2 \pi k n / w} \right) = M_{k_i, j} \left( e^{i P_{k_i, j}} \right)
 \end{equation}
@@
 \begin{equation}
-  \text{SWS}_{\ell}\left({M_k}\right)_j = \sum_{n = 0}^{\ell-1} M_{k, j+n}
+  \text{SWS}_{\ell}\left({M_k}\right)_j = \sum_{n = 0}^{\ell-1} M_{k_i, j+n}
 \end{equation}
@@
   \label{eq:objfn}
-  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( \left( \sum_{n = 0}^{\ell-1} \hat{M}_{k_i, j+n} \right) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k, j} - \hat{M}_{k, j} \right)^2
+  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( \left( \sum_{n = 0}^{\ell-1} \hat{M}_{k_i, j+n} \right) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k_i, j} - \hat{M}_{k_i, j} \right)^2
 \end{equation}
@@
   \includegraphics[width=\columnwidth]{WindowEffect.pdf}
-  \caption{This figure shows the effect of varying $\ell$ for a fixed $\lambda=0.1$.
+  \caption{This figure shows the effect of varying $\ell$ for a fixed $\lambda=0.1$, using the lowest two non-DC frequencies to embed each coordinate.
 A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive compression, but an $\ell$ that's too large can over-smooth.}
@@
   \includegraphics[width=\columnwidth]{LambdaEffect.pdf}
-  \caption{This figure shows the effect of varying $\lambda$ for a fixed $\ell=16$.
+  \caption{This figure shows the effect of varying $\lambda$ for a fixed $\ell=16$, embedding using the lowest two non-DC frequencies to.
 A smaller $\lambda$ in Equation~\ref{eq:objfn} leads to higher geometric fidelity (Goal~\ref{goal:geomquality}), at the cost of audio quality (Goal~\ref{goal:imperceptible}), as measured by SNR.}
@@
 
-subject to $\hat{M_{k, j}} \geq 0$.
+subject to $\hat{M_{k_i, j}} \geq 0$.
 In other words, we want the magnitude SW-STFT of a perturbed signal to match the target coordinate as well as possible, while preserving the original audio as well as possible, according to $\lambda$.
@@
 
+After solving for $\hat{M_{k_i, j}}$, we replace all rows of $M_{k_i}$ with $\hat{M_{k_i}}$, and we perform an inverse STFT of $M e^{i P}$ for the original phases $P$ (Section~\ref{sec:componentscales} will explain when it is necessary to modify the phases as well).
+We can then save the resulting audio in a compressed format, and recover the hidden signal by loading it in and extracting the corresponding components of the magnitude SW-STFT.
+
 \subsubsection{Computational Complexity}
 \label{sec:computation}
-Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem, and there are myriad algorithms for solving such systems efficiently via repeated evaluation of the linear system and its adjoint.
+Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem, and there are myriad algorithms \cite{branch1999subspace} for solving such systems efficiently via repeated evaluation of the linear system and its adjoint on iterative estimates of a solution .
 Furthermore, though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function at each iteration, the linear operator and its adjoint can be implemented with $O(N)$ operations only, independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}.
@@
   \label{eq:cumusum}
-  C_{k, j} = \sum_{i=j}^{j+\ell} \hat{M_{k, i}}
+  C_{k_i, j} = \sum_{i=j}^{j+\ell} \hat{M_{k, i}}
 \end{equation}
@@
   \label{eq:objfncumusum}
-  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( (C_{k, j+\ell}-C_{k, j}) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k, j} - \hat{M}_{k, j} \right)^2
+  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( (C_{k_i, j+\ell}-C_{k_i, j}) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k_i, j} - \hat{M}_{k_i, j} \right)^2
 \end{equation}
@@
 
-In general, the SWS-STFT sequence $X$ will not have the same number of samples as the target $T$.  If we stick to scenarios where $T$ has more samples, we can index $X$ by a default function
+In general, the SWS-STFT sequence will not have the same number of samples as the target $T$.  If we stick to scenarios where $T$ has more samples, we can index $X$ by a default function
 
@@
   \includegraphics[width=\columnwidth]{OptimalShift.pdf}
-  \caption{Curve length can be used as a proxy for distortion.}
-  \label{fig:TSPTour}
+  \caption{Curve length can be used as a proxy for distortion, so a shift which minimizes curve length is most likely the shift needed to re-align audio to frame windows.
+The dot here indicates the ground truth shift of an embedding using the lowest two non-DC frequencies with $\lambda=0.1, \ell=16$, and the global mins exactly match ground truth.}
+  \label{fig:FrameAlignments}
 \end{figure}
+
+What we've described so far works for audio that's aligned to each window, but additional work needs to be done to address Goal ~\ref{goal:misalignment} if the audio to decode comes in misaligned.
+To this end, we can use the fact that the curves don't jump very far from sample to sample; a TSP tour is defined as length-minimizing, and adjacent samples in Hamiltonian cycles on meshes move only between neighboring triangles on the original mesh.
+Therefore, if the embedding is frame aligned, the length of the curve should be minimized.
+Conversely, if the embedding is not frame aligned, the curve becomes noisy and is more likely to jump around quickly from sample to sample.
+Figure~\ref{fig:FrameAlignments}
 

### 2022-11-13 writeup/paper.tex
Adding viterbi figure and starting to write up about viterbi warps.  Also some corrections/edits throughout

@@
     \item \label{goal:misalignment} The hidden data should be robust to frame misalignment, or it should be possible to recover a frame alignment without any prior information
+    \item \label{goal:metadata} No metadata should be required to retrieve the hidden data; (compressed) audio alone should suffice
     \item \label{goal:partial} It should be possible to recover the data partially from partial audio chunks; that is, we don't need to wait for the entire data stream to recover the signal
@@
   \includegraphics[width=\columnwidth]{CurvatureShortening.png}
-  \caption{Anticipating that mp3 compression will introduce noise to our embedded curves, we pre-smooth them before hiding them using one application of curvature-shortening flow, which smooths the curves without introducing any crossings.
+  \caption{Anticipating that mp3 compression will introduce noise to our embedded curves, we pre-smooth them before hiding them using one iteration of curvature-shortening flow, which smooths the curves without introducing any crossings.
 We find $\sigma=1$ to be a good tradeoff between smoothness and detail.}
@@
 
-where $c_1$ and $c_2$ are appropriate normalization constants.  Then we can estimate the arc length of a sampled curve $\gamma[j]$ with the rectangular integral of a smoothed velocity estimate:
+where $c_1$ and $c_2$ are appropriate normalization constants.  Then we estimate the arc length of a sampled curve $\gamma[j]$ with the rectangular integral of a smoothed velocity estimate:
 
@@
 
-In addition to 2D TSP tours on stipple patterns on planar images, we can also create artistic 3D space curves that fill out the surfaces of 3D shapes following the technique of Gopi and Epstein \cite{gopi2004single}.
+In addition to 2D TSP tours on stipple patterns on planar images, we also create artistic 3D space curves that fill out the surfaces of 3D shapes following the technique of Gopi and Epstein \cite{gopi2004single}.
 They observe that watertight triangle meshes (those with no boundary) have a dual graph in which a perfect matching exists.
@@
 In practice, we use the Blossom-5 algorithm \cite{kolmogorov2009blossom} to find perfect matches of the dual graph.
-Then, adding edges between unpaired triangles leads to a set of disconnected cycles (third column of Figure~\ref{fig:HamiltonianHorse}), which can be connected by a spanning set of edges between paired triangles.
-Finally, the spanning edges can be split into bridges between the cycles disconnected cycles, joining them together into one large cycle that covers the surface of the triangle mesh.
+Then, adding edges between unpaired triangles leads to a set of disconnected cycles (third column of Figure~\ref{fig:HamiltonianHorse}), which are connected by a spanning set of edges between paired triangles.
+Finally, the spanning edges are split into bridges between the disconnected cycles, joining them together into one large cycle that covers the surface of the triangle mesh.
 
@@
 Before we go into the details, we first define quantitative measurements for measuring the fit to the original audio (Goal~\ref{goal:imperceptible}) and the geometric quality of the hidden curve (Goal~\ref{goal:geomquality}).
+Let the original carrier audio be $x_i$ and let the steganography audio be $y_i$.
+Then the steganographic signal to noise ratio is define as
 
@@
   \caption{This figure shows the effect of varying $\ell$ for a fixed $\lambda=0.1$, using the lowest two non-DC frequencies to embed each coordinate.
-A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive compression, but an $\ell$ that's too large can over-smooth.}
+A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive compression, but an $\ell$ that's too large may over-smooth.}
   \label{fig:WindowEffect}
@@
 After solving for $\hat{M_{k_i, j}}$, we replace all rows of $M_{k_i}$ with $\hat{M_{k_i}}$, and we perform an inverse STFT of $M e^{i P}$ for the original phases $P$ (Section~\ref{sec:componentscales} will explain when it is necessary to modify the phases as well).
-We can then save the resulting audio in a compressed format, and recover the hidden signal by loading it in and extracting the corresponding components of the magnitude SW-STFT.
+We then save the resulting audio in a compressed format, and recover the hidden signal by loading it in and extracting the corresponding components of the magnitude SW-STFT.
 
@@
 \label{sec:computation}
-Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem, and there are myriad algorithms \cite{branch1999subspace} for solving such systems efficiently via repeated evaluation of the linear system and its adjoint on iterative estimates of a solution .
-Furthermore, though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function at each iteration, the linear operator and its adjoint can be implemented with $O(N)$ operations only, independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}.
-For example, let
-
-\begin{equation}
-  \label{eq:cumusum}
-  C_{k_i, j} = \sum_{i=j}^{j+\ell} \hat{M_{k, i}}
-\end{equation}
-
-then Equation~\ref{eq:objfn} can be rewritten as 
+Minimizing equation~\ref{eq:objfn} can be formulated as a sparse nonnegative linear least squares problem, and there are myriad algorithms (e.g.
+\cite{branch1999subspace}) for solving such systems efficiently via repeated evaluation of the linear system and its adjoint on iterative estimates of a solution .
+Furthermore, though Equation~\ref{eq:objfn} suggest an $O(N \ell)$ time complexity to evaluate the objective function at each iteration, we implement the linear operator and its adjoint with $O(N)$ operations only, independent of $\ell$, using the 1D version of the ``summed area tables'' trick in computer vision \cite{lewisfast}.
+For example, let $C_{k_i, j} = \sum_{i=0}^{j} \hat{M_{k, i}}$, and $C_{k_i, j < 1} = 0$.
+Then Equation~\ref{eq:objfn} can be rewritten as
 \begin{equation}
   \label{eq:objfncumusum}
-  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( (C_{k_i, j+\ell}-C_{k_i, j}) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k_i, j} - \hat{M}_{k_i, j} \right)^2
+  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( (C_{k_i, j+\ell-1}-C_{k_i, j-1}) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k_i, j} - \hat{M}_{k_i, j} \right)^2
 \end{equation}
@@
 \subsubsection{The choice of non-overlapping windows}
-Though some other works use transforms with overlapping windows (\cite{hwan_sik_yun_acoustic_2010,geleta_pixinwav_2021}), we find that changing different STFT bins independently can lead to STFTs that do not correspond to any real signal due to discrepancies between overlapping windows.
+Though some other works use transforms with overlapping windows \cite{hwan_sik_yun_acoustic_2010,geleta_pixinwav_2021}, changing different STFT bins independently leads to STFTs that do not correspond to any real signal due to discrepancies between overlapping windows.
 An algorithm like Griffin-Lim \cite{griffin1984signal} can recover a signal whose spectrogram has a locally minimal distance to the perturbed STFT, but we find that this step introduces an unacceptable level of distortion both in the target and the carrier audio.
 This problem occurs even for real-valued transforms such as the Discrete Cosine Transform (which was used by \cite{geleta_pixinwav_2021}).
-We sidestep this problem completely by using non-overlapping windows as in \cite{xiaoxiao_dong_data_2004}.
+Like \cite{xiaoxiao_dong_data_2004}, we sidestep this problem by using non-overlapping windows.
 
@@
 
-\subsection{Rescaling And Re-Parameterizing Targets for Better Fits}
+\subsection{Shifting, Scaling And Re-Parameterizing Targets for Better Fits}
 \label{sec:reparam}
 
-A crucial step to keep the hidden signal imperceptible is to rescale the targets to match the dynamic range of the signals.
-Unfortunately, we lose relative scale information between the components, but we will explain how to store and recover this in Section~\ref{sec:componentscales}
+\subsubsection{Vertical Translation/Scaling}
 
-In general, the SWS-STFT sequence will not have the same number of samples as the target $T$.  If we stick to scenarios where $T$ has more samples, we can index $X$ by a default function
+A crucial step to keep the hidden signal imperceptible is to shift and rescale the target coordinates of the hidden curve to match the dynamic range of the SW-STFT components.
+This way, the STFT magnitudes don't have to be perturbed as much to match the target.
+Let $\text{SWS}_{\ell}\left({M_{k+i}}\right)$ be the $i^{\text{th}}$ frequency coordinate of the SW-STFT of the carrier signal, and let $T_i[m]$ be the $m^{\text{th}}$ coordinate of the $i^{\text{th}}$ dimension of the target curve.
+We first choose a scale ratio $a_i$ for each component as the ratio of the standard deviations $\text{stdev}_j \left( \text{SWS}_{\ell} ({M_{k+i}})[j] \right) / \text{stdev}_j (T_i[j])$.
+Then, letting $N$ be the length of the two signals, we choose the vertical shift $b_i$ as
+
+\begin{equation}
+  b_i = \frac{1}{N} \sum_{j=1}^N  \text{SWS}_{\ell} ({M_{k+i}})[j] - T_i[j]
+\end{equation}
+
+the rescaled target $\hat{T}$ is then defined as $\hat{T_i}[j] = a_i T_i[j] + b_i$.
+Unfortunately, we do lose relative scale information between the components, but we will explain how to hide and recover this in Section~\ref{sec:componentscales}
+
+\subsubsection{Viterbi Re-Parameterization}
+Beyond shifting and scaling the targets coordinates vertically, we may also need to re-parameterize them in time, since, in general, the SWS-STFT sequence will not have the same number of samples as the target $T$.
+Let $M$ be the number of samples of the SW-STFT and $N$ be the number of samples of the target, and assume that $N > M$.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{Viterbi.pdf}
+  \caption{Starting at a different place on the target loop and traversing it at a non-uniform speed traces out the same shape, while matching the given SW-STFT better.}
+  \label{fig:ViterbiWarp}
+\end{figure}
 
@@
   \includegraphics[width=\columnwidth]{OptimalShift.pdf}
-  \caption{Curve length can be used as a proxy for distortion, so a shift which minimizes curve length is most likely the shift needed to re-align audio to frame windows.
+  \caption{A shift which minimizes curve length is most likely the shift needed to re-align audio to frame windows.
 The dot here indicates the ground truth shift of an embedding using the lowest two non-DC frequencies with $\lambda=0.1, \ell=16$, and the global mins exactly match ground truth.}
@@
 What we've described so far works for audio that's aligned to each window, but additional work needs to be done to address Goal ~\ref{goal:misalignment} if the audio to decode comes in misaligned.
-To this end, we can use the fact that the curves don't jump very far from sample to sample; a TSP tour is defined as length-minimizing, and adjacent samples in Hamiltonian cycles on meshes move only between neighboring triangles on the original mesh.
+To this end, we use the fact that the curves don't jump very far from sample to sample; a TSP tour is defined as length-minimizing, and adjacent samples in Hamiltonian cycles on meshes move only between neighboring triangles on the original mesh.
 Therefore, if the embedding is frame aligned, the length of the curve should be minimized.

### 2022-11-13 viewer/audio.js
Almost finished 2D viewer, except still need to scale by phase

@@ -1,0 +1,131 @@
+/**
+ * Create audio samples in the wav format
+ * @param {array} channels Array arrays of audio samples
+ * @param {int} sr Sample rate
+ */
+function createWavURL(channels, sr) {
+    const nChannels = channels.length;
+    const N = channels[0].length;
+    let audio = new Float32Array(N*nChannels);
+    // Interleave audio channels
+    for (let i = 0; i < N; i++) {
+      for (let j = 0; j < nChannels; j++) {
+        audio[i*nChannels+j] = channels[j][i];
+      }
+    }
+
+    // get WAV file bytes and audio params of your audio source
+    const wavBytes = getWavBytes(audio.buffer, {
+      isFloat: true,       // floating point or 16-bit integer
+      numChannels: nChannels,
+      sampleRate: sr,
+    })
+    const wav = new Blob([wavBytes], {type: 'audio/wav'});
+    return window.URL.createObjectURL(wav);
+}
+
+
+class SampledAudio {
+  constructor(audioPlayer) {
+    this.mediaRecorder = null;
+    this.audio = null;
+    this.recorder = null;
+    this.audioPlayer = audioPlayer;
+
+    this.audioBlob = null;
+    this.channels = [];
+    this.sr = 44100;
+    this.audioContext = new AudioContext({sampleRate:this.sr});
+    this.setupMenu();
+
+  }
+
+  setupMenu() {
+    let shaderObj = this;
+    let menu = new dat.GUI();
+    this.menu = menu;
+    this.folders = [];
+  }
+
+
+  /**
+   * Set the audio samples based on an array buffer
+   * @param {ArrayBuffer} data Array buffer with audio data
+   * @param {DOM Element} canvasArea Handle to the canvas div where canvases
+   *                                 can be added
+   * @param {string} colormap Default colormap to use
+   * @returns 
+   */
+  setSamplesAudioBuffer(data, canvasArea, colormap) {
+    let that = this;
+    return new Promise(resolve => {
+      that.audioContext.decodeAudioData(data, function(buff) {
+        that.channels = [];
+        for (let i = 0; i < buff.numberOfChannels; i++) {
+          that.channels.push(buff.getChannelData(i));
+        }
+        that.sr = buff.sampleRate;
+        that.audioPlayer.src = createWavURL(that.channels, that.sr);
+
+        // Remove previous menus
+        for (let i = 0; i < that.folders.length; i++) {
+          that.menu.removeFolder(that.folders[i]);
+        }
+        that.folders = [];
[…]

### 2022-11-13 viewer/colormaps.js

@@ -1,0 +1,17 @@
+let colormaps = {};
+colormaps.copper = [[0.3, 0.3, 0.3], [0.30581, 0.1934, 0.12316], [0.30969, 0.19585, 0.12472], [0.3155, 0.19952, 0.12706], [0.31938, 0.20197, 0.12863], [0.32519, 0.20565, 0.13097], [0.32907, 0.2081, 0.13253], [0.33488, 0.21178, 0.13487], [0.34069, 0.21545, 0.13721], [0.34457, 0.2179, 0.13877], [0.35038, 0.22158, 0.14111], [0.35426, 0.22403, 0.14267], [0.36007, 0.22771, 0.14501], [0.36394, 0.23016, 0.14657], [0.36976, 0.23383, 0.14892], [0.37557, 0.23751, 0.15126], [0.37945, 0.23996, 0.15282], [0.38526, 0.24364, 0.15516], [0.38913, 0.24609, 0.15672], [0.39495, 0.24977, 0.15906], [0.40076, 0.25344, 0.1614], [0.40464, 0.25589, 0.16296], [0.41045, 0.25957, 0.1653], [0.41433, 0.26202, 0.16686], [0.42014, 0.2657, 0.16921], [0.42401, 0.26815, 0.17077], [0.42983, 0.27182, 0.17311], [0.43564, 0.2755, 0.17545], [0.43952, 0.27795, 0.17701], [0.44533, 0.28163, 0.17935], [0.4492, 0.28408, 0.18091], [0.45502, 0.28775, 0.18325], [0.45889, 0.2902, 0.18481], [0.46471, 0.29388, 0.18715], [0.47052, 0.29756, 0.1895], [0.47439, 0.30001, 0.19106], [0.48021, 0.30368, 0.1934], [0.48408, 0.30613, 0.19496], [0.4899, 0.30981, 0.1973], [0.49377, 0.31226, 0.19886], [0.49958, 0.31594, 0.2012], [0.5054, 0.31961, 0.20354], [0.50927, 0.32206, 0.2051], [0.51509, 0.32574, 0.20744], [0.51896, 0.32819, 0.20901], [0.52478, 0.33187, 0.21135], [0.52865, 0.33432, 0.21291], [0.53446, 0.33799, 0.21525], [0.54028, 0.34167, 0.21759], [0.54415, 0.34412, 0.21915], [0.54997, 0.3478, 0.22149
[…]

### 2022-11-13 viewer/colormaps.py

@@ -1,0 +1,18 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import json
+import skimage.color
+
+s = "let colormaps = {};\n"
+
+for colormap in ["copper", "Spectral", "spring", "summer", "autumn", "winter", "ocean", "magma", "viridis", "RdBu", "PiYG", "PRGn", "BrBG", "PuOr", "RdGy"]:
+    c = plt.get_cmap(colormap)
+    C = c(np.array(np.round(np.linspace(0, 255, 100)), dtype=np.int32))
+    C = C[:, 0:3]
+    C = skimage.color.rgb2hsv(C)
+    C[:, 2] = 0.3 + 0.4*C[:, 2]
+    C = skimage.color.hsv2rgb(C)
+    C = np.round(C, 5)
+    C = C.tolist()
+    s += "colormaps.{} = {};\n".format(colormap, C)
+print(s)

### 2022-11-13 viewer/dspworker.js

@@ -1,0 +1,64 @@
+onmessage = function(event) {
+    const samples = event.data.samples;
+    const win = event.data.win;
+    const L = event.data.L;
+    const freqs = event.data.freqs;
+    // Step 1: Setup cosine and sine windows
+    postMessage({"type":"newTask", "taskString":"Setting up windows"});
+    let cos = [];
+    let sin = [];
+    for (let i = 0; i < freqs.length; i++) {
+        let cosi = new Float32Array(win);
+        let sini = new Float32Array(win);
+        for (let j = 0; j < win; j++) {
+            cosi[j] = Math.cos(2*Math.PI*freqs[i]*j/win);
+            sini[j] = Math.sin(2*Math.PI*freqs[i]*j/win);
+        }
+        cos.push(cosi);
+        sin.push(sini);
+    }
+
+    // Step 2: Compute spectrogram at chosen bins
+    postMessage({"type":"newTask", "taskString":"Computing spectrogram"});
+    let M = Math.floor(samples.length/win);
+    let SM = []; // Magnitudes
+    let SP = []; // Phases
+    for (let i = 0; i < freqs.length; i++) {
+        let SMi = new Float32Array(M);
+        let SPi = new Float32Array(M);
+        for (let j = 0; j < M; j++) {
+            let cosSum = 0;
+            let sinSum = 0;
+            for (let k = 0; k < win; k++) {
+                cosSum += samples[j*win+k]*cos[i][k];
+                sinSum += samples[j*win+k]*sin[i][k];
+            }
+            SMi[j] = Math.sqrt(cosSum*cosSum + sinSum*sinSum);
+            SPi[j] = Math.atan2(sinSum, cosSum);
+        }
+        SM.push(SMi);
+        SP.push(SPi);
+    }
+
+    // Step 3: Compute sliding window using cumulative sums
+    postMessage({"type":"newTask", "taskString":"Computing sliding window of magnitudes for " + freqs.length + " frequencies"});
+    let coords = [];
+    M = SM[0].length;
+    for (let i = 0; i < freqs.length; i++) {
+        let N = M-L+1;
+        let coordsi = new Float32Array(N);
+        let cumu = new Float32Array(M+1);
+        cumu[0] = 0;
+        for (let j = 0; j < M; j++) {
+            cumu[j+1] = cumu[j] + SM[i][j];
+        }
+        for (let j = 0; j < N; j++) {
[…]

### 2022-11-13 viewer/jslibs/base64-arraybuffer.js

@@ -1,0 +1,67 @@
+var b64arraybuffer;
+(function(){function r(e,n,t){function o(i,f){if(!n[i]){if(!e[i]){var c="function"==typeof require&&require;if(!f&&c)return c(i,!0);if(u)return u(i,!0);var a=new Error("Cannot find module '"+i+"'");throw a.code="MODULE_NOT_FOUND",a}var p=n[i]={exports:{}};e[i][0].call(p.exports,function(r){var n=e[i][1][r];return o(n||r)},p,p.exports,r,e,n,t)}return n[i].exports}for(var u="function"==typeof require&&require,i=0;i<t.length;i++)o(t[i]);return o}return r})()({1:[function(require,module,exports){
+b64arraybuffer = require('base64-arraybuffer');
+},{"base64-arraybuffer":2}],2:[function(require,module,exports){
+/*
+ * base64-arraybuffer 1.0.1 <https://github.com/niklasvh/base64-arraybuffer>
+ * Copyright (c) 2021 Niklas von Hertzen <https://hertzen.com>
+ * Released under MIT License
+ */
+(function (global, factory) {
+    typeof exports === 'object' && typeof module !== 'undefined' ? factory(exports) :
+    typeof define === 'function' && define.amd ? define(['exports'], factory) :
+    (global = typeof globalThis !== 'undefined' ? globalThis : global || self, factory(global['base64-arraybuffer'] = {}));
+}(this, (function (exports) { 'use strict';
+
+    var chars = 'ABCDEFGHIJKLMNOPQRSTUVWXYZabcdefghijklmnopqrstuvwxyz0123456789+/';
+    // Use a lookup table to find the index.
+    var lookup = typeof Uint8Array === 'undefined' ? [] : new Uint8Array(256);
+    for (var i = 0; i < chars.length; i++) {
+        lookup[chars.charCodeAt(i)] = i;
+    }
+    var encode = function (arraybuffer) {
+        var bytes = new Uint8Array(arraybuffer), i, len = bytes.length, base64 = '';
+        for (i = 0; i < len; i += 3) {
+            base64 += chars[bytes[i] >> 2];
+            base64 += chars[((bytes[i] & 3) << 4) | (bytes[i + 1] >> 4)];
+            base64 += chars[((bytes[i + 1] & 15) << 2) | (bytes[i + 2] >> 6)];
+            base64 += chars[bytes[i + 2] & 63];
+        }
+        if (len % 3 === 2) {
[…]

### 2022-11-13 viewer/main.js

@@ -1,0 +1,14 @@
+let tuneInput = document.getElementById('tuneInput');
+let audioPlayer = document.getElementById("audioPlayer");
+let audio = new SampledAudio(audioPlayer);
+const canvasArea = document.getElementById("canvasArea");
+
+tuneInput.addEventListener('change', function(e) {
+    let reader = new FileReader();
+    reader.onload = function(e) {
+        audio.setSamplesAudioBuffer(e.target.result, canvasArea);
+    }
+    reader.readAsArrayBuffer(tuneInput.files[0]);
+});
+
+audio.loadFile("baby.mp3", canvasArea);

### 2022-11-13 viewer/progressbar.js

@@ -1,0 +1,60 @@
+/**
+ * Code copyright Christopher J. Tralie, 2021
+ * Attribution-NonCommercial-ShareAlike 4.0 International
+ */
+
+/**
+ * A class to show loading progress
+ */
+
+function ProgressBar() {
+    //A function to show a progress bar
+    this.loading = false;
+    this.loadString = "Loading";
+    this.loadColor = "#cccc00";
+    this.ndots = 0;
+    this.waitingDisp = document.getElementById("pagestatus");
+    this.startLoading = function(message) {
+        if (message === undefined) {
+            this.loadString = "Loading";
+        }
+        else {
+            this.loadString = message;
+        }
+        this.loading = true;
+        this.changeLoad();
+    }
+    this.changeMessage = function(message) {
+        this.loadString = message;
+        this.waitingDisp.innerHTML = "<font color = \"" + this.loadColor + "\">" + this.loadString;
+    }
+    this.changeLoad = function() {
+        if (!this.loading) {
+            return;
+        }
+        var s = "<font color = \"" + this.loadColor + "\">" + this.loadString;
+        for (var i = 0; i < this.ndots; i++) {
+            s += ".";
+        }
+        s += "</font>";
+        this.waitingDisp.innerHTML = s;
+        if (this.loading) {
+            this.ndots = (this.ndots + 1)%12;
+            setTimeout(this.changeLoad.bind(this), 200);
+        }
+    };
+    this.changeToReady = function(message) {
+        this.loading = false;
+        if (message === undefined) {
+            message = "Ready";
+        }
+        this.waitingDisp.innerHTML = "<font color = \"#009900\">" + message + "</font>";
+    };
+    this.setLoadingFailed = function(message) {
+        if (message === undefined) {
+            message = "Loading Failed :(";
+        }
+        this.loading = false;
+        this.waitingDisp.innerHTML = "<font color = \"red\">" + message + "</font>";
+    };
+}

### 2022-11-13 viewer/stegcanvas.js

@@ -1,0 +1,474 @@
+const VERT_SRC = `
+attribute vec3 a_info;
+attribute vec3 a_color;
+
+// Uniforms set from Javascript that are constant
+// over all fragments
+uniform vec2 uCenter; // Where the origin (0, 0) is on the canvas
+uniform float uScale; // Scale of fractal
+uniform float uPointSize; // Size to draw points
+
+varying float v_time;
+varying vec3 v_color;
+
+void main() {
+  gl_PointSize = uPointSize;
+  vec2 a_position = vec2(a_info.x, a_info.y);
+  gl_Position = vec4((a_position-uCenter)*uScale, 0, 1);
+  v_time = a_info.z;
+  v_color = a_color;
+}`;
+
+const FRAG_SRC = `
+precision highp float;
+
+varying float v_time;
+varying vec3 v_color;
+uniform float uTime;
+
+void main() {
+    gl_FragColor = vec4(v_color, 1);
+}`;
+
+
+getMousePos = function(evt) {
+    if ('touches' in evt) {
+        return {
+            X: evt.touches[0].clientX,
+            Y: evt.touches[1].clientY
+        }
+    }
+    return {
+        X: evt.clientX,
+        Y: evt.clientY
+    };
+}
+
+/**
+ * A function that compiles a particular shader
+ * @param {object} gl WebGL handle
+ * @param {string} shadersrc A string holding the GLSL source code for the shader
+ * @param {string} type The type of shader ("fragment" or "vertex") 
+ * 
+ * @returns{shader} Shader object
+ */
+function getShader(gl, shadersrc, type) {
+    var shader;
+    if (type == "fragment") {
+        shader = gl.createShader(gl.FRAGMENT_SHADER);
+    } 
+    else if (type == "vertex") {
+        shader = gl.createShader(gl.VERTEX_SHADER);
+    } 
+    else {
+        return null;
+    }
+    
+    gl.shaderSource(shader, shadersrc);
+    gl.compileShader(shader);
+
+    if (!gl.getShaderParameter(shader, gl.COMPILE_STATUS)) {
+        console.log("Unable to compile " + type + " shader...")
+        console.log(shadersrc);
+        console.log(gl.getShaderInfoLog(shader));
+        alert("Could not compile shader");
+        return null;
+    }
+    return shader;
+}
+
+
+/**
+ * Compile a vertex shader and a fragment shader and link them together
+ * 
+ * @param {object} gl WebGL Handle
[…]

### 2022-11-13 viewer/wav.js

@@ -1,0 +1,68 @@
+// From https://stackoverflow.com/questions/62172398/convert-audiobuffer-to-arraybuffer-blob-for-wav-download
+
+// Returns Uint8Array of WAV bytes
+function getWavBytes(buffer, options) {
+  const type = options.isFloat ? Float32Array : Uint16Array
+  const numFrames = buffer.byteLength / type.BYTES_PER_ELEMENT
+
+  const headerBytes = getWavHeader(Object.assign({}, options, { numFrames }))
+  const wavBytes = new Uint8Array(headerBytes.length + buffer.byteLength);
+
+  // prepend header, then add pcmBytes
+  wavBytes.set(headerBytes, 0)
+  wavBytes.set(new Uint8Array(buffer), headerBytes.length)
+
+  return wavBytes
+}
+
+// adapted from https://gist.github.com/also/900023
+// returns Uint8Array of WAV header bytes
+function getWavHeader(options) {
+  const numFrames =      options.numFrames
+  const numChannels =    options.numChannels || 2
+  const sampleRate =     options.sampleRate || 44100
+  const bytesPerSample = options.isFloat? 4 : 2
+  const format =         options.isFloat? 3 : 1
+
+  const blockAlign = numChannels * bytesPerSample
+  const byteRate = sampleRate * blockAlign
+  const dataSize = numFrames * blockAlign
+
+  const buffer = new ArrayBuffer(44)
+  const dv = new DataView(buffer)
+
+  let p = 0
+
+  function writeString(s) {
+    for (let i = 0; i < s.length; i++) {
+      dv.setUint8(p + i, s.charCodeAt(i))
+    }
+    p += s.length
+  }
+
+  function writeUint32(d) {
+    dv.setUint32(p, d, true)
+    p += 4
+  }
+
+  function writeUint16(d) {
+    dv.setUint16(p, d, true)
+    p += 2
+  }
+
+  writeString('RIFF')              // ChunkID
+  writeUint32(dataSize + 36)       // ChunkSize
+  writeString('WAVE')              // Format
+  writeString('fmt ')              // Subchunk1ID
+  writeUint32(16)                  // Subchunk1Size
+  writeUint16(format)              // AudioFormat
+  writeUint16(numChannels)         // NumChannels
+  writeUint32(sampleRate)          // SampleRate
+  writeUint32(byteRate)            // ByteRate
+  writeUint16(blockAlign)          // BlockAlign
[…]

### 2022-11-13 viewer/audio.js
Finished scaling by phase

@@ -1,3 +1,5 @@
+const WINDOW_FAC = 0.7;
+
 /**
  * Create audio samples in the wav format
  * @param {array} channels Array arrays of audio samples
@@ -76,7 +78,7 @@ class SampledAudio {
         // Setup canvases
         canvasArea.innerHTML = ""; // Clear prior canvases
 
-        let width = Math.min(window.innerWidth, window.innerHeight);
+        let width = WINDOW_FAC*Math.min(window.innerWidth, window.innerHeight);
         let folder = that.menu.addFolder("Parameters");
         that.folders.push(folder);
         let canvas = document.createElement("canvas");

### 2022-11-13 viewer/dspworker.js

@@ -2,6 +2,7 @@ onmessage = function(event) {
     const samples = event.data.samples;
     const win = event.data.win;
     const L = event.data.L;
+    const Q = event.data.Q;
     const freqs = event.data.freqs;
     // Step 1: Setup cosine and sine windows
     postMessage({"type":"newTask", "taskString":"Setting up windows"});
@@ -57,6 +58,50 @@ onmessage = function(event) {
         }
         coords.push(coordsi);
     }
+
+    // Step 4: Normalize and scale by phase
+    postMessage({"type":"newTask", "taskString":"Normalizing"});
+    // Step 4a: Rescale each coordinate to [-1, 1]
+    for (let i = 0; i < freqs.length; i++) {
+        let min = coords[i][0];
+        for (let j = 0; j < coords[i].length; j++) {
+            if (coords[i][j] < min) {
+                min = coords[i][j];
+            }
+        }
+        let max = coords[i][0];
+        for (let j = 0; j < coords[i].length; j++) {
+            coords[i][j] -= min;
+            if (coords[i][j] > max) {
+                max = coords[i][j];
+            }
+        }
+        for (let j = 0; j < coords[i].length; j++) {
+            coords[i][j] = coords[i][j]*2/max - 1;
+        }
+    }
+    // Step 4b: Compute means of each phase
+    const inc = 2*Math.PI/Q;
+    let scales = new Float32Array(freqs.length);
+    for (let i = 0; i < freqs.length; i++) {
+        scales[i] = 0;
+        for (let j = 0; j < SP[i].length; j++) {
+            let p = SP[i][j];
+            let plow = 2*(p - inc*Math.floor(p/inc))/inc;
+            let phigh = 2*(inc*Math.ceil(p/inc) - p)/inc;
+            p = Math.min(plow, phigh);
+            scales[i] += p;
+        }
+        scales[i] /= SP[i].length;
+        scales[i] = (scales[i]-0.25)*2;
+    }
+    // Step 4c: Perform final scaling
+    for (let i = 0; i < scales.length; i++) {
+        for (let j = 0; j < coords[i].length; j++) {
+            coords[i][j] *= scales[i];
+        }
+    }
+    
 
     // Return results
     postMessage({"type":"end", "coords":coords});

### 2022-11-13 viewer/stegcanvas.js

@@ -144,6 +144,7 @@ class StegCanvas2D {
         this.scale = 1;
         this.win = 1024;
         this.L = 16;
+        this.Q = 4;
         this.freq1 = 1;
         this.freq2 = 2;
         
@@ -191,9 +192,10 @@ class StegCanvas2D {
         };
         this.progressBar = new ProgressBar();
         this.folder = folder;
-        this.stippleSize = 1;
-        folder.add(this, "win").onChange(this.extractSignal.bind(this));
-        folder.add(this, "L").onChange(this.extractSignal.bind(this));
+        this.stippleSize = 0.2;
+        folder.add(this, "win", 0, this.sr, 1).onChange(this.extractSignal.bind(this));
+        folder.add(this, "L", 0).onChange(this.extractSignal.bind(this));
+        folder.add(this, "Q", 1, 10, 1).onChange(this.extractSignal.bind(this));
         folder.add(this, "freq1", 0, Math.floor(this.win/2), 1).onChange(this.extractSignal.bind(this));
         folder.add(this, "freq2", 0, Math.floor(this.win/2), 1).onChange(this.extractSignal.bind(this));
         folder.add(this, "stippleSize", 0.1, 4).onChange(repaint);
@@ -239,7 +241,7 @@ class StegCanvas2D {
         const progressBar = this.progressBar;
         new Promise((resolve, reject) => {
             const worker = new Worker("dspworker.js");
-            let payload = {samples:that.audioSamples, win:that.win, L:that.L, freqs:[this.freq1, this.freq2]};
+            let payload = {samples:that.audioSamples, win:that.win, L:that.L, Q:that.Q, freqs:[this.freq1, this.freq2]};
             worker.postMessage(payload);
             worker.onmessage = function(event) {
                 if (event.data.type == "newTask") {
@@ -281,39 +283,10 @@ class StegCanvas2D {
         // Setup position and time buffers
         const N = this.x.length;
         let info = new Float32Array(N*3);
-        // Normalize to square
-        let x = [];
-        let y = [];
-        let mins = [this.x[0], this.y[0]];
-        for (let i = 0; i < N; i++) {
-            x[i] = this.x[i];
-            y[i] = this.y[i];
-            if (x[i] < mins[0]) {
-                mins[0] = x[i];
-            }
-            if (y[i] < mins[1]) {
-                mins[1] = y[i];
-            }
-        }
[…]

### 2022-11-15 writeup/paper.tex
Adding 2D examples

@@
 Beyond shifting and scaling the targets coordinates vertically, we may also need to re-parameterize them in time, since, in general, the SWS-STFT sequence will not have the same number of samples as the target $T$.
-Let $M$ be the number of samples of the SW-STFT and $N$ be the number of samples of the target, and assume that $N > M$.
+Let $M$ be the number of samples of the SW-STFT and $N$ be the number of samples of the target, and assume that $N > M$ (we can always resample our target curves to make this true).
 
@@
 
+\algrenewcommand\algorithmicindent{0.8em}%
+\begin{algorithm}
+  \caption{Stipple Tunes Algorithm}
+
+  \begin{algorithmic}[1]
+    \Procedure{StippleTune}{$Z$, $x$, na, win, tw} \Comment{$Z$ is stipple, $x$ is audio samples, {\em na} is number of discrete angle states, {\em win} is number of samples between angle states, and {\em tw} is amount by which angle can jump each step}
+    \State $N \gets \text{len}(x)$ \Comment{Number of audio samples}
+    \State $Y \gets x + ix$
+    \State Setup a KDTree {\em tree} for fast NN queries on $Z$
+    \State $M \gets \text{ceil}(N / \text{win})$
+    \State $C[i, 0] \gets 0, C[i, j > 1] \gets \infty$ \Comment{$na \times M$ Cumulative cost matrix}
+    \State $I[i, j] \gets 0$ \Comment{$na \times M$ backpointers to best preceding state}
+    \For{$t = 2:M$}
+        \For{$j = 1:na$}
+            \State $\theta_j \gets 2 \pi j / \text{na}$
+            \For{$k = j-\text{tw}:j-1 \mod \text{na}$}
+                \State $\theta_k \gets 2 \pi k / \text{na}$ \label{lst:line:interpolate}
+                \State Let $\theta_{\ell} \gets \theta_j + (\theta_k-\theta_j)/\text{win}$ 
+                \State $d \gets \sum_{\ell = 1}^{\text{win}} \text{tree.query}(Y[\text{win}*t + \ell] e^{i \theta_{\ell}})$ \Comment{Sum nearest neighbors of all points}
+                \If{$C[k, t-1] + d < C[j, t]$}
+                    \State $C[j, t] \gets C[k, t-1] + d$ 
+                    \State $I[j, t] \gets k$  \Comment{Remember optimal transition}
+                \EndIf
+            \EndFor
+        \EndFor
+    \EndFor \\
+    \State Backtrace $I$ to obtain the optimal sequence of angle states
+    \State Linearly interpolate between each angle state (line~\ref{lst:line:interpolate}) to compute $\theta[k], k = 1 \text{ to } N$ 
+    \State Let $X_k$ be the nearest neighbor in $Z$ to $Y_k e^{i \theta[k]}$, using {\em tree} to speed up queries \\
+    \Return $X$
+    \EndProcedure
+  \end{algorithmic}
+  \label{alg:stippletunes}
+\end{algorithm}
+
 Our use of the Viterbi algorithm for re-parameterizing geometric sequences is related to the technique for corpus-based concatenative synthesis presented by the authors of \cite{schwarz2007corpus}.
@@
 As a rule of thumb, we find that having a target curve with about 1.5-2x as many samples as there are SWS-STFT frames gives enough wiggle room for the Viterbi algorithm.
-Therefore, in our experiments in Section~\ref{sec:experiments}, we will generate TSP and Hamiltonian sequences with 2000 samples for our 1200-1300 SWS-STFT frames
+In our experiments in Section~\ref{sec:experiments}, we will generate TSP and Hamiltonian sequences with 2000 samples for our 1200-1300 SWS-STFT frames
 

### 2022-11-15 src/stego.py

@@ -256,46 +256,6 @@ def viterbi_loop_trace(csm, K):
     path.reverse()
     return path
 
-def get_best_target(X, Y, K):
-    """
-    Return the best path through a target, traversing it in either direction
-
-    Parameters
-    ----------
-    X: ndarray(M, 2)
-        Target states
-    Y: ndarray(N, 2)
-        Time points
-    K: int
-        Maximum jump interval between states
-    """
-    costfn = lambda Z: np.sum(np.abs(Z-Y))
-
-    min_path = np.arange(Y.shape[0]) % X.shape[0]
-    min_cost = costfn(X[min_path, :])
-
-    # Try default orientation
-    csm = np.abs(X[:, 0][:, None] - Y[:, 0][None, :])
-    csm += np.abs(X[:, 1][:, None] - Y[:, 1][None, :])
-    path = viterbi_loop_trace(csm, K)
-    path = np.array(path, dtype=int)
-    cost = costfn(X[path, :])
-    if cost < min_cost:
-        min_cost = cost
-        min_path = path
-    
-    # Try reverse orientation
-    csm = np.abs(X[:, 0][:, None] - Y[::-1, 0][None, :])
-    csm += np.abs(X[:, 1][:, None] - Y[::-1, 1][None, :])
-    path = viterbi_loop_trace(csm, K)
-    path = X.shape[0]-1-np.array(path, dtype=int)
-    cost = costfn(X[path, :])
-    if cost < min_cost:
-        min_cost = cost
-        min_path = path
-
-    return min_path, min_cost
-
 def make_voronoi_image(coords, phases):
     from scipy.spatial import KDTree
     phases = np.abs(phases)

### 2022-11-15 viewer/audio.js

@@ -55,10 +55,10 @@ class SampledAudio {
    * @param {ArrayBuffer} data Array buffer with audio data
    * @param {DOM Element} canvasArea Handle to the canvas div where canvases
    *                                 can be added
-   * @param {string} colormap Default colormap to use
+   * @param {object} params Default audio parameters
    * @returns 
    */
-  setSamplesAudioBuffer(data, canvasArea, colormap) {
+  setSamplesAudioBuffer(data, canvasArea, params) {
     let that = this;
     return new Promise(resolve => {
       that.audioContext.decodeAudioData(data, function(buff) {
@@ -85,7 +85,7 @@ class SampledAudio {
         canvas.width=width;
         canvas.height=width;
         canvasArea.appendChild(canvas);
-        new StegCanvas2D(canvas, that.audioPlayer, that.channels[0], that.sr, folder, colormap);
+        that.stegCanvas = new StegCanvas2D(canvas, that.audioPlayer, that.channels[0], that.sr, folder, params);
         resolve();
       });
     });

### 2022-11-15 viewer/colormaps.js

@@ -1,6 +1,6 @@
 let colormaps = {};
-colormaps.copper = [[0.3, 0.3, 0.3], [0.30581, 0.1934, 0.12316], [0.30969, 0.19585, 0.12472], [0.3155, 0.19952, 0.12706], [0.31938, 0.20197, 0.12863], [0.32519, 0.20565, 0.13097], [0.32907, 0.2081, 0.13253], [0.33488, 0.21178, 0.13487], [0.34069, 0.21545, 0.13721], [0.34457, 0.2179, 0.13877], [0.35038, 0.22158, 0.14111], [0.35426, 0.22403, 0.14267], [0.36007, 0.22771, 0.14501], [0.36394, 0.23016, 0.14657], [0.36976, 0.23383, 0.14892], [0.37557, 0.23751, 0.15126], [0.37945, 0.23996, 0.15282], [0.38526, 0.24364, 0.15516], [0.38913, 0.24609, 0.15672], [0.39495, 0.24977, 0.15906], [0.40076, 0.25344, 0.1614], [0.40464, 0.25589, 0.16296], [0.41045, 0.25957, 0.1653], [0.41433, 0.26202, 0.16686], [0.42014, 0.2657, 0.16921], [0.42401, 0.26815, 0.17077], [0.42983, 0.27182, 0.17311], [0.43564, 0.2755, 0.17545], [0.43952, 0.27795, 0.17701], [0.44533, 0.28163, 0.17935], [0.4492, 0.28408, 0.18091], [0.45502, 0.28775, 0.18325], [0.45889, 0.2902, 0.18481], [0.46471, 0.29388, 0.18715], [0.47052, 0.29756, 0.1895], [0.47439, 0.30001, 0.19106], [0.48021, 0.30368, 0.1934], [0.48408, 0.30613, 0.19496], [0.4899, 0.30981, 0.1973], [0.49377, 0.31226, 0.19886], [0.49958, 0.31594, 0.2012], [0.5054, 0.31961, 0.20354], [0.50927, 0.32206, 0.2051], [0.51509, 0.32574, 0.20744], [0.51896, 0.32819, 0.20901], [0.52478, 0.33187, 0.21135], [0.52865, 0.33432, 0.21291], [0.53446, 0.33799, 0.21525], [0.54028, 0.34167, 0.21759], [0.54415, 0.34412, 0.21915], [0.54997, 0.3478, 0.22
[…]

### 2022-11-15 viewer/dspworker.js

@@ -96,9 +96,15 @@ onmessage = function(event) {
         scales[i] = (scales[i]-0.25)*2;
     }
     // Step 4c: Perform final scaling
+    let maxScaleIdx = 0;
+    for (let i = 1; i < scales.length; i++) {
+        if (scales[i] > scales[maxScaleIdx]) {
+            maxScaleIdx = i;
+        }
+    }
     for (let i = 0; i < scales.length; i++) {
         for (let j = 0; j < coords[i].length; j++) {
-            coords[i][j] *= scales[i];
+            coords[i][j] *= scales[i]/scales[maxScaleIdx];
         }
     }
     

### 2022-11-15 viewer/main.js

@@ -11,4 +11,4 @@ tuneInput.addEventListener('change', function(e) {
     reader.readAsArrayBuffer(tuneInput.files[0]);
 });
 
-audio.loadFile("baby.mp3", canvasArea);
+audio.loadFile("examples/usher-baby-2d.mp3", canvasArea);

### 2022-11-15 viewer/stegcanvas.js

@@ -1,3 +1,5 @@
+let DSP_WORKER_PATH = "dspworker.js";
+
 const VERT_SRC = `
 attribute vec3 a_info;
 attribute vec3 a_color;
@@ -129,9 +131,9 @@ class StegCanvas2D {
      * @param {Float32Array} audioSamples Audio samples
      * @param {int} sr Sample rate
      * @param {Dat.GUI Folder} folder Handle to dat.gui folder for options
-     * @param {string} colormap Default colormap to use
+     * @param {object} params Default parameters to use
      */
-    constructor(glcanvas, audioPlayer, audioSamples, sr, folder, colormap) {
+    constructor(glcanvas, audioPlayer, audioSamples, sr, folder, params) {
         this.audioPlayer = audioPlayer;
         this.audioSamples = audioSamples;
         this.sr = sr;
@@ -140,13 +142,21 @@ class StegCanvas2D {
         this.colorBuffers = {};
 
         // Viewing options
+        if (params === undefined) {
+            params = {};
+        }
         this.centervec = [0, 0];
         this.scale = 1;
-        this.win = 1024;
-        this.L = 16;
-        this.Q = 4;
-        this.freq1 = 1;
-        this.freq2 = 2;
+        let defaultParams = {"win":1024, "L":16, "Q":4, "freq1":1, "freq2":2, "colormap":"Spectral"};
+        for (let param in defaultParams) {
+            if (param in params) {
+                this[param] = params[param];
+            }
+            else {
+                this[param] = defaultParams[param];
+            }
+        }
+        let colormap = this.colormap;
         
         try {
             glcanvas.gl = glcanvas.getContext("webgl");
@@ -240,7 +250,7 @@ class StegCanvas2D {
         const that = this;
         const progressBar = this.progressBar;
         new Promise((resolve, reject) => {
-            const worker = new Worker("dspworker.js");
+            const worker = new Worker(DSP_WORKER_PATH);
             let payload = {samples:that.audioSamples, win:that.win, L:that.L, Q:that.Q, freqs:[this.freq1, this.freq2]};
             worker.postMessage(payload);
             worker.onmessage = function(event) {
@@ -267,8 +277,7 @@ class StegCanvas2D {
                 }
             }
         }).then(() => {
-            progressBar.changeToReady();
-            progressBar.changeMessage("Ready!  Press play!");
+            progressBar.changeToReady("Ready!  Press play!");
         }).catch(reason => {
             progressBar.setLoadingFailed(reason);
         });

### 2022-11-15 writeup/paper.tex
Finished first crack at viterbi algorithm description

--- 2022-11-13 writeup/paper.tex
@@
 %
-\usepackage{cite,url,amsfonts}
+\usepackage{cite,url,amsfonts,amsmath}
 \usepackage{algorithm}% http://ctan.org/pkg/algorithms
@@
 % \renewcommand\UrlFont{\color{blue}\rmfamily}
-
+\DeclareMathOperator*{\argmin}{arg\,min}
 \graphicspath{{figs/}, {../figures/}}
@@
 
+In this section, we explain how to modify the target curves to better match the given SW-STFT so that the STFT magnitudes don't have to be perturbed as much for the SW-STFT to match the target, leading to a less noticeable embedding of the hidden curve for the same quality geometry.
+
 \subsubsection{Vertical Translation/Scaling}
@@
 A crucial step to keep the hidden signal imperceptible is to shift and rescale the target coordinates of the hidden curve to match the dynamic range of the SW-STFT components.
-This way, the STFT magnitudes don't have to be perturbed as much to match the target.
-Let $\text{SWS}_{\ell}\left({M_{k+i}}\right)$ be the $i^{\text{th}}$ frequency coordinate of the SW-STFT of the carrier signal, and let $T_i[m]$ be the $m^{\text{th}}$ coordinate of the $i^{\text{th}}$ dimension of the target curve.
-We first choose a scale ratio $a_i$ for each component as the ratio of the standard deviations $\text{stdev}_j \left( \text{SWS}_{\ell} ({M_{k+i}})[j] \right) / \text{stdev}_j (T_i[j])$.
+Let $\text{SWS}_{\ell}\left({M_{k_i}}\right)$ be the $k_i^{\text{th}}$ frequency coordinate of the SW-STFT of the carrier signal, and let $T_i[m]$ be the $m^{\text{th}}$ coordinate of the $i^{\text{th}}$ dimension of the target curve.
+We first choose a scale ratio $a_i$ for each component as the ratio of the standard deviations $\text{stdev}_j \left( \text{SWS}_{\ell} ({M_{k_i}})[j] \right) / \text{stdev}_j (T_i[j])$.
 Then, letting $N$ be the length of the two signals, we choose the vertical shift $b_i$ as
@@
 \begin{equation}
-  b_i = \frac{1}{N} \sum_{j=1}^N  \text{SWS}_{\ell} ({M_{k+i}})[j] - T_i[j]
+  b_i = \frac{1}{N} \sum_{j=1}^N  \text{SWS}_{\ell} ({M_{k_i}})[j] - T_i[j]
 \end{equation}
 
-the rescaled target $\hat{T}$ is then defined as $\hat{T_i}[j] = a_i T_i[j] + b_i$.
-Unfortunately, we do lose relative scale information between the components, but we will explain how to hide and recover this in Section~\ref{sec:componentscales}
+the rescaled target coordinate $\hat{T_i}$ is then defined as $\hat{T_i}[j] = a_i T_i[j] + b_i$.
+Unfortunately, we lose relative scale information between the components, but we will explain how to hide and recover this in Section~\ref{sec:componentscales}
 
-\subsubsection{Viterbi Re-Parameterization}
-Beyond shifting and scaling the targets coordinates vertically, we may also need to re-parameterize them in time, since, in general, the SWS-STFT sequence will not have the same number of samples as the target $T$.
-Let $M$ be the number of samples of the SW-STFT and $N$ be the number of samples of the target, and assume that $N > M$.
+\subsubsection{Viterbi Target Re-Parameterization}
+
+\algrenewcommand\algorithmicindent{0.8em}%
+\begin{algorithm}
+  \caption{Viterbi Target Re-Parameterization}
+
+  \begin{algorithmic}[1]
+    \Procedure{ViterbiTargetReparam}{$\hat{T}$, $\text{SWS}_{\ell} ({M})$, $K$}
+    \State $N_T \gets \text{len}(\hat{T})$ \Comment{Number of target points}
+    \State $N_M \gets \text{len}(\text{SWS}_{\ell}({M}))$ \Comment{Number of SW-STFT frames}
+    \State $S[i, j] \gets 0$ \Comment{$N_T \times N_M$ Cumulative cost matrix}
+    \State $S[1, j] \gets \sum_{i=1}^d (\hat{T}_i[1] - \text{SWS}_{\ell} ({M_{k_i}})[j])^2$
+    \State $B[i, j] \gets 0$ \Comment{$N_T \times N_M$ backpointers to best preceding states}
+    \For{$j = 2:N_M$}
+        \For{$t = 1:N_T$}
+            \State $S[t, j] = \min_{k=(t-K) \mod N_T} ^ {k=(t-1) \mod N_T} S[k, j-1] $ \Comment {Find best preceding state}
+            \State $S[t, j] \gets S[t, j] + \sum_{i=1}^d (\hat{T}_i[t] - \text{SWS}_{\ell} ({M_{k_i}})[j])^2$ \Comment{Add on matching cost}
+            \State $B[t, j] = \argmin_{k=(t-K) \mod N_T} ^ {k=(t-1) \mod N_T} S[k, j-1] $ \Comment {Save reference to best preceding state}
+        \EndFor
+    \EndFor
+    \State Backtrace $B$ to obtain the optimal sequence $\Theta$ \\
+    \Return $\Theta$
+    \EndProcedure
+  \end{algorithmic}
+  \label{alg:viterbiwarp}
+\end{algorithm}
+
+Beyond shifting and scaling the targets coordinates vertically, we may also need to re-parameterize them in time, since, in general, the SWS-STFT sequence will not have the same number of samples as the shifted target $\hat{T}$.
+Furthermore, the target curves are cyclic, so the starting point is arbitrary, nor does it matter if we traverse the curve left or right.
+This gives us a lot of freedom in how we choose to re-parameterize the target to best match the signal even before we perturb the signal.
+Let $N_M$ be the number of frames in the SW-STFT and $N_T$ be the number of samples of the target, and assume that $N_T > N_M$ (we can always resample our target curves to make this true).
+Let $\Theta = \{ \theta_1, \theta_2, \theta_3, \hdots, \theta_{N_M} \}$ be new indices into the target, and let $K > 0$ be a positive integer so that $1 \leq (\theta_i - \theta_{i-1}) \mod N_T \leq K$; that is, $K$ chooses the maximum number of samples by which the target re-parameterization can jump in adjacent time steps.
+We seek a $\Theta$ minimizing the following objective function for a $d$-dimensional shifted target $\hat{T}$
+
+\begin{equation}
+  \label{eq:viterbiobj}
+  g(\Theta = \{\theta_1, \theta_2, \hdots, \theta_{N_M}\}) = \sum_{j = 1}^{N_M} \sum_{i=1}^d \left( \text{SWS}_{\ell} ({M_{k_i}})[\theta_j] - \hat{T}_i[j]  \right)^2
+\end{equation}
+
+For a fixed $K$, we use the Viterbi algorithm to obtain a $\Theta$ minimizing Equation~\ref{eq:viterbiobj} in $O(MNK)$ time.
+Our use of the Viterbi algorithm for re-parameterizing geometric sequences is similar to the technique for corpus-based concatenative synthesis presented by the authors of \cite{schwarz2007corpus}.
+Algorithm~\ref{alg:viterbiwarp} gives more details.
 
@@
   \includegraphics[width=\columnwidth]{Viterbi.pdf}
-  \caption{Starting at a different place on the target loop and traversing it at a non-uniform speed traces out the same shape, while matching the given SW-STFT better.}
+  \caption{Starting at a different place on the target loop and traversing it at a non-uniform speed traces out the same shape, while matching the given SW-STFT better than a uniform parameterization starting at an artibrary place on the target.}
   \label{fig:ViterbiWarp}
@@
 
-Our use of the Viterbi algorithm for re-parameterizing geometric sequences is related to the technique for corpus-based concatenative synthesis presented by the authors of \cite{schwarz2007corpus}.
-
+In practice, we re-run the algorithm starting at $K = 1$, and we repeatedly increment $K$ until the optimal $\Theta$ goes through at least one full loop on the target.
+Since clockwise or counter-clockwise traversal of the target is arbitrary, we then rerun this procedure again for a reversed version of the sequence and keep the result which minimizes Equation~\ref{eq:viterbiobj}.
 As a rule of thumb, we find that having a target curve with about 1.5-2x as many samples as there are SWS-STFT frames gives enough wiggle room for the Viterbi algorithm.
-Therefore, in our experiments in Section~\ref{sec:experiments}, we will generate TSP and Hamiltonian sequences with 2000 samples for our 1200-1300 SWS-STFT frames
+In our experiments in Section~\ref{sec:experiments}, we will generate TSP and Hamiltonian sequences with 2000 samples for our 1200-1300 SWS-STFT frames.
+Figure~\ref{fig:ViterbiWarp} shows an example running this algorithm under these conditions on the Usher example in column 3 of Figure~\ref{fig:WindowEffect}.
 

### 2022-11-15 src/stego.py

@@ -229,8 +229,8 @@ def viterbi_loop_trace(csm, K):
     list(N)
         State indices of best fit cyclic path
     """
-    M = csm.shape[0]
-    N = csm.shape[1]
+    M = csm.shape[0] # N_T
+    N = csm.shape[1] # N_M
     S = np.zeros((M, N))
     S[:, 0] = csm[:, 0]
     B = np.zeros((M, N)) # Backpointers

### 2022-11-15 writeup/paper.tex
Objective functions

@@
 Before we go into the details, we first define quantitative measurements for measuring the fit to the original audio (Goal~\ref{goal:imperceptible}) and the geometric quality of the hidden curve (Goal~\ref{goal:geomquality}).
-Let the original carrier audio be $x_i$ and let the steganography audio be $y_i$.
-Then the steganographic signal to noise ratio is define as
+Let the original carrier audio be $x$ and let the steganography audio be $y$, each with $N$ samples.
+Then the steganographic signal to noise ratio in decibels (dB) is define as
+
+\begin{equation}
+  \label{eq:stegsnr}
+   \text{snr}(y|x) = \left( \frac{ \log_{10}\left( \frac{1}{N} \sum_{j=1}^N x_j^2 \right) }{ \log_{10}\left( \frac{1}{N} \sum_{j=1}^N (y_j-x_j)^2 \right) } \right)
+\end{equation}
+
+For our geometric measurement of quality, let $X_i$ be a sequence of $M$ target curve points in $\mathbb{R}^d$ and $Y_i$ be a sequence of $M$ reconstructed points in $\mathbb{R}^d$.
+Then the {\em mean geometric distortion} is defined simply as the mean Euclidean distance between these points
+
+\begin{equation}
+  \label{eq:distortion}
+  \text{distortion}(Y|X) = \frac{1}{M} \sum_{j=1}^M ||X_j - Y_j||_2
+\end{equation}
+
+We seek to find a balance between minimizing Equation~\ref{eq:stegsnr} and Equation~\ref{eq:distortion}.  We now formulate an objective function that trades both of them off.
 
@@
 subject to $\hat{M_{k_i, j}} \geq 0$.
-In other words, we want the magnitude SW-STFT of a perturbed signal to match the target coordinate as well as possible, while preserving the original audio as well as possible, according to $\lambda$.
+In other words, we want the magnitude SW-STFT of a perturbed signal to match the target coordinate as well as possible (minimize Equation~\ref{eq:distortion}), while preserving the original audio as well as possible (minimizing Equation~\ref{eq:viterbiobj}), according to $\lambda$.
 A greater $\lambda$ means that the signal will fit the original audio better, at the cost of a noisier curve.
@@
 
-What we've described so far works for audio that's aligned to each window, but additional work needs to be done to address Goal ~\ref{goal:misalignment} if the audio to decode comes in misaligned.
-To this end, we use the fact that the curves don't jump very far from sample to sample; a TSP tour is defined as length-minimizing, and adjacent samples in Hamiltonian cycles on meshes move only between neighboring triangles on the original mesh.
-Therefore, if the embedding is frame aligned, the length of the curve should be minimized.
+What we've described so far works for audio that is aligned to each window, but additional work needs to be done to address Goal ~\ref{goal:misalignment} if the audio to decode comes in misaligned.
+To this end, we use the fact that the curves move only slightly between adjacent samples; a TSP tour is defined as length-minimizing, and adjacent samples in Hamiltonian cycles on meshes move only between neighboring triangles on the original mesh.
+If the embedding is frame aligned, the length of the curve should be minimized.
 Conversely, if the embedding is not frame aligned, the curve becomes noisy and is more likely to jump around quickly from sample to sample.
-Figure~\ref{fig:FrameAlignments}
+Therefore, we can pick the alignment which minimizes the length in all possible shifts from $0$ to $win$.
+Figure~\ref{fig:FrameAlignments} shows an example.
+We will empirically evaluate this in Section~\ref{sec:experiments}.
 
@@
 
+Talk about how this scheme works for any orthogonal decomposition of the signal and how we tried wavelets
+
 %

### 2022-11-15 writeup/paper.tex
Cleaning up notation and fixing some mistakes

@@
 Let the original carrier audio be $x$ and let the steganography audio be $y$, each with $N$ samples.
-Then the steganographic signal to noise ratio in decibels (dB) is define as
+Then we define the steganographic signal to noise ratio in decibels (dB) as
 
@@
   \label{eq:stegsnr}
-   \text{snr}(y|x) = \left( \frac{ \log_{10}\left( \frac{1}{N} \sum_{j=1}^N x_j^2 \right) }{ \log_{10}\left( \frac{1}{N} \sum_{j=1}^N (y_j-x_j)^2 \right) } \right)
+   \text{snr}(y|x) = 10  \log_{10} \left(\sum_{j=1}^N x_j^2 \right) -  10 \log_{10}\left(\sum_{j=1}^N (y_j-x_j)^2  \right)
 \end{equation}
@@
 For our geometric measurement of quality, let $X_i$ be a sequence of $M$ target curve points in $\mathbb{R}^d$ and $Y_i$ be a sequence of $M$ reconstructed points in $\mathbb{R}^d$.
-Then the {\em mean geometric distortion} is defined simply as the mean Euclidean distance between these points
+Then we define the {\em mean geometric distortion} is simply as the mean Euclidean distance between these points
 
@@
 
-We seek to find a balance between minimizing Equation~\ref{eq:stegsnr} and Equation~\ref{eq:distortion}.  We now formulate an objective function that trades both of them off.
-
 \subsection{Formulation of Least Squares Problem}
 
-Let $T = (T_1, T_2, \hdots, T_N \}$ the desired Euclidean target point sequence to hide, where each $T_i \in \mathbb{R}^d$, and $T_i[m]$ refers to the $m^{\text{th}}$ coordinate of $T_i$, and let $x$ be a set of audio samples which will serve as a carrier.
+We now formulate an objective function that trades off Equation~\ref{eq:stegsnr} and Equation~\ref{eq:distortion}.
+Let $T = (T_1, T_2, \hdots, T_N \}$ be the sequence of points of the target curve to hide, where each $T_i \in \mathbb{R}^d$, and let $T_{i, m}$ refer to $m^{\text{th}}$ coordinate of $T_i$, and let $x$ be a set of audio samples which will serve as a carrier.
 The goal is to perturb the samples of $x$ so that some function of $x$ matches $T$ as closely as possible.
@@
 \begin{equation}
-  S_{k_i, j} = \sum_{n = 0}^w x_{jw + n} \left(e^{-i 2 \pi k n / w} \right) = M_{k_i, j} \left( e^{i P_{k_i, j}} \right)
+  S_{k, j} = \sum_{n = 0}^w x_{jw + n} \left(e^{-i 2 \pi k n / w} \right) = M_{k, j} \left( e^{i P_{k, j}} \right)
 \end{equation}
@@
 and we factor $S$ it into its magnitude and phase components $M$ and $P$, respectively.
-Then, given a second window length $\ell$, we define the following {\em sliding window sum} function, which we apply to each row $k$ of the magnitudes of $S$ that we wish to perturb to obtain the SWS-STFT
+Next, we choose a subset of $d$ frequencies $k_i$, each of which will hide a different dimension of $T$.
+Given a second window length $\ell$, we then define the following {\em sliding window sum} function, which we apply to each row $k_i$ of the magnitudes of $S$ that we wish to perturb to obtain the SWS-STFT
 
 \begin{equation}
-  \text{SWS}_{\ell}\left({M_k}\right)_j = \sum_{n = 0}^{\ell-1} M_{k_i, j+n}
+  \text{SWS}^{\ell}(M)_{k_i, j} = \sum_{n = 0}^{\ell-1} M_{k_i, j+n}
 \end{equation}
 
-The effect of $\ell$ is to smooth out the noisy time series at each row $k$ of the magnitude spectrogram so that the rows in the SW-STFT match smoother transitions in the target curves.
-The resulting time series $\text{SWS}_{\ell}\left({M_k}\right)$ has $N-\ell+1$ samples.
-Let's assume momentarily that $T$ has exactly this many samples; we will address the case where $len(T) > N-\ell+1$ in Section~\ref{sec:reparam}.
-We then seek a perturbed version of the magnitudes, $\hat{M}$ so that each coordinate $i$ is hidden in a single frequency index $k_i$ of $\hat{M}$.
+The effect of $\ell$ is to smooth out the noisy rows $k_i$ of the magnitude spectrogram so that the rows in the SW-STFT match smoother transitions in the target curves.
+Each row of the SW-STFT has $N-\ell+1$ samples.
+Let's assume momentarily that $T$ has exactly this many samples; we will address the case where $\text{length}(T) > N-\ell+1$ in Section~\ref{sec:reparam}.
+We then seek a perturbed version of the magnitudes $\hat{M}$ so that each coordinate $i$ is hidden in a single frequency index $k_i$ of $\hat{M}$.
 To that end, we minimize the following objective function, one coordinate dimension $i = 1, ...
@@
   \label{eq:objfn}
-  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( \left( \sum_{n = 0}^{\ell-1} \hat{M}_{k_i, j+n} \right) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k_i, j} - \hat{M}_{k_i, j} \right)^2
+  f(\hat{M}_{k_i}) = \sum_{j=1}^{N-\ell+1} \left( \left( \sum_{n = 0}^{\ell-1} \hat{M}_{k_i, j+n} \right) - T_{i, j} \right)^2 + \lambda \sum_{j=1}^N \left( M_{k_i, j} - \hat{M}_{k_i, j} \right)^2
 \end{equation}
@@
 subject to $\hat{M_{k_i, j}} \geq 0$.
-In other words, we want the magnitude SW-STFT of a perturbed signal to match the target coordinate as well as possible (minimize Equation~\ref{eq:distortion}), while preserving the original audio as well as possible (minimizing Equation~\ref{eq:viterbiobj}), according to $\lambda$.
+In other words, we want the magnitude SW-STFT of a perturbed signal to match the target coordinate as well as possible (minimizing Equation~\ref{eq:distortion}), while preserving the original audio as well as possible (minimizing Equation~\ref{eq:viterbiobj}), according to $\lambda$.
 A greater $\lambda$ means that the signal will fit the original audio better, at the cost of a noisier curve.
-Figure~\ref{fig:LambdaEffect} shows an example of varying $\lambda$.
+Figure~\ref{fig:LambdaEffect} shows an example.
 
@@
   \label{eq:objfncumusum}
-  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( (C_{k_i, j+\ell-1}-C_{k_i, j-1}) - T_i[j] \right)^2 + \lambda \sum_{j=1}^N \left( M_{k_i, j} - \hat{M}_{k_i, j} \right)^2
+  f_i(\hat{M}) = \sum_{j=1}^{N-\ell+1} \left( (C_{k_i, j+\ell-1}-C_{k_i, j-1}) - T_{i, j} \right)^2 + \lambda \sum_{j=1}^N \left( M_{k_i, j} - \hat{M}_{k_i, j} \right)^2
 \end{equation}
@@
 A crucial step to keep the hidden signal imperceptible is to shift and rescale the target coordinates of the hidden curve to match the dynamic range of the SW-STFT components.
-Let $\text{SWS}_{\ell}\left({M_{k_i}}\right)$ be the $k_i^{\text{th}}$ frequency coordinate of the SW-STFT of the carrier signal, and let $T_i[m]$ be the $m^{\text{th}}$ coordinate of the $i^{\text{th}}$ dimension of the target curve.
-We first choose a scale ratio $a_i$ for each component as the ratio of the standard deviations $\text{stdev}_j \left( \text{SWS}_{\ell} ({M_{k_i}})[j] \right) / \text{stdev}_j (T_i[j])$.
+We first choose a scale ratio $a_i$ for each component as the ratio of the standard deviations $\text{stdev}_j \left( \text{SWS}^{\ell} (M)_{k_i, j} \right) / \text{stdev}_j (T_{i, j})$.
 Then, letting $N$ be the length of the two signals, we choose the vertical shift $b_i$ as
@@
 \begin{equation}
-  b_i = \frac{1}{N} \sum_{j=1}^N  \text{SWS}_{\ell} ({M_{k_i}})[j] - T_i[j]
+  b_i = \frac{1}{N} \sum_{j=1}^N  \text{SWS}^{\ell} (M)_{k_i, j} - T_{i, j}
 \end{equation}
 
-the rescaled target coordinate $\hat{T_i}$ is then defined as $\hat{T_i}[j] = a_i T_i[j] + b_i$.
+The rescaled target coordinate $\hat{T_i}$ is then defined as $\hat{T}_{i, j} = a_i T_{i, j} + b_i$.
 Unfortunately, we lose relative scale information between the components, but we will explain how to hide and recover this in Section~\ref{sec:componentscales}
@@
   \begin{algorithmic}[1]
-    \Procedure{ViterbiTargetReparam}{$\hat{T}$, $\text{SWS}_{\ell} ({M})$, $K$}
+    \Procedure{ViterbiTargetReparam}{$\hat{T}$, $\text{SWS}^{\ell} (M)$, $K$}
     \State $N_T \gets \text{len}(\hat{T})$ \Comment{Number of target points}
-    \State $N_M \gets \text{len}(\text{SWS}_{\ell}({M}))$ \Comment{Number of SW-STFT frames}
-    \State $S[i, j] \gets 0$ \Comment{$N_T \times N_M$ Cumulative cost matrix}
-    \State $S[1, j] \gets \sum_{i=1}^d (\hat{T}_i[1] - \text{SWS}_{\ell} ({M_{k_i}})[j])^2$
+    \State $N_M \gets \text{len}(\text{SWS}^{\ell}(M))$ \Comment{Number of SW-STFT frames}
+    \State $S[i>1, j] \gets 0$ \Comment{$N_T \times N_M$ Cumulative cost matrix}
+    \State $S[1, j] \gets \sum_{i=1}^d (\hat{T}_{i, 1} - \text{SWS}^{\ell} (M)_{k_i, j})^2$
     \State $B[i, j] \gets 0$ \Comment{$N_T \times N_M$ backpointers to best preceding states}
@@
             \State $S[t, j] = \min_{k=(t-K) \mod N_T} ^ {k=(t-1) \mod N_T} S[k, j-1] $ \Comment {Find best preceding state}
-            \State $S[t, j] \gets S[t, j] + \sum_{i=1}^d (\hat{T}_i[t] - \text{SWS}_{\ell} ({M_{k_i}})[j])^2$ \Comment{Add on matching cost}
+            \State $S[t, j] \gets S[t, j] + \sum_{i=1}^d (\hat{T}_{i, t} - \text{SWS}^{\ell} (M)_{k_i, j})^2$ \Comment{Add on matching cost}
             \State $B[t, j] = \argmin_{k=(t-K) \mod N_T} ^ {k=(t-1) \mod N_T} S[k, j-1] $ \Comment {Save reference to best preceding state}
@@
 Let $N_M$ be the number of frames in the SW-STFT and $N_T$ be the number of samples of the target, and assume that $N_T > N_M$ (we can always resample our target curves to make this true).
-Let $\Theta = \{ \theta_1, \theta_2, \theta_3, \hdots, \theta_{N_M} \}$ be new indices into the target, and let $K > 0$ be a positive integer so that $1 \leq (\theta_i - \theta_{i-1}) \mod N_T \leq K$; that is, $K$ chooses the maximum number of samples by which the target re-parameterization can jump in adjacent time steps.
+Let $\Theta = \{ \theta_1, \theta_2, \theta_3, \hdots, \theta_{N_M} \}$ be new indices into the target, and let $K > 0$ be a positive integer so that $1 \leq \left( (\theta_i - \theta_{i-1}) \mod N_T \right) \leq K$; that is, $K$ is the maximum number of samples by which the target re-parameterization can jump in adjacent time steps.
 We seek a $\Theta$ minimizing the following objective function for a $d$-dimensional shifted target $\hat{T}$
@@
   \label{eq:viterbiobj}
-  g(\Theta = \{\theta_1, \theta_2, \hdots, \theta_{N_M}\}) = \sum_{j = 1}^{N_M} \sum_{i=1}^d \left( \text{SWS}_{\ell} ({M_{k_i}})[\theta_j] - \hat{T}_i[j]  \right)^2
+  g(\Theta = \{\theta_1, \theta_2, \hdots, \theta_{N_M}\}) = \sum_{j = 1}^{N_M} \sum_{i=1}^d \left( \text{SWS}^{\ell} (M)_{k_i, j} - \hat{T}_{i, j}  \right)^2
 \end{equation}

### 2022-11-15 writeup/paper.tex
Adding most of experiment figures

@@
 We first choose a scale ratio $a_i$ for each component as the ratio of the standard deviations $\text{stdev}_j \left( \text{SWS}^{\ell} (M)_{k_i, j} \right) / \text{stdev}_j (T_{i, j})$.
-Then, letting $N$ be the length of the two signals, we choose the vertical shift $b_i$ as
+Then, letting $N$ be the length of the two signals, we compute the vertical shift $b_i$ as
 
 \begin{equation}
-  b_i = \frac{1}{N} \sum_{j=1}^N  \text{SWS}^{\ell} (M)_{k_i, j} - T_{i, j}
+  b_i = \frac{1}{N} \sum_{j=1}^N  \text{SWS}^{\ell} (M)_{k_i, j} - a_i T_{i, j}
 \end{equation}
@@
   \includegraphics[width=\columnwidth]{Viterbi.pdf}
-  \caption{Starting at a different place on the target loop and traversing it at a non-uniform speed traces out the same shape, while matching the given SW-STFT better than a uniform parameterization starting at an artibrary place on the target.}
+  \caption{Circularly shifting the target loop and traversing it at a non-uniform speed traces out the same shape, while matching the given SW-STFT better than a uniform parameterization starting at an artibrary place on the target.}
   \label{fig:ViterbiWarp}
@@
 What we've described so far works for audio that is aligned to each window, but additional work needs to be done to address Goal ~\ref{goal:misalignment} if the audio to decode comes in misaligned.
-To this end, we use the fact that the curves move only slightly between adjacent samples; a TSP tour is defined as length-minimizing, and adjacent samples in Hamiltonian cycles on meshes move only between neighboring triangles on the original mesh.
+To this end, we use the fact that the hidden curves move only slightly between adjacent samples; a TSP tour is defined as length-minimizing, and adjacent samples in Hamiltonian cycles on meshes move only between neighboring triangles on the original mesh.
 If the embedding is frame aligned, the length of the curve should be minimized.
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{CaltechGTzanFixedLam.pdf}
+  \includegraphics[width=\columnwidth]{MeshSegGTzanFixedLam.pdf}
+  \caption{The results embedding curves into clips from the Tzanetakis genre dataset varying the window length $\ell$ for a fixed $\lambda$.
+Moderate window lengths are the best choices for both SNR and distortion.
+We recommend $\ell=16$.}
+  \label{fig:ResultsFixedLam}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{CaltechGTzanFixedWin.pdf}
+  \includegraphics[width=\columnwidth]{MeshSegGTzanFixedWin.pdf}
+  \caption{The results embedding curves into clips from the Tzanetakis genre dataset, for a fixed $\ell=16$.
+As expected from Equation~\ref{eq:objfn}, both the distortion and SNR go up as $\lambda$ increases.}
+  \label{fig:ResultsFixedWin}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{CaltechGTzanViterbiExperiment.pdf}
+  \includegraphics[width=\columnwidth]{MeshSegGtzanViterbiExperiment.pdf}
+  \caption{Pre-warping the target with Viterbi alignment (Section~\ref{sec:reparam}) overall improves the resulting distortion and SNR.}
+  \label{fig:ResultsViterbiExperiment}
+\end{figure}
+
+As Figure~\ref{fig:ResultsFixedLam} shows, increasing the window length has a positive effect on geometric distortion, while moderate window lengths lead to the best SNR.
+
 \subsection{Subjective Listening Experiment}
@@
   \includegraphics[width=0.8\columnwidth]{Turk.pdf}
-  \caption{Results of the listening experiment on the Amazon Mechanical Turk}
+  \caption{Results of the listening experiment on the Amazon Mechanical Turk.  A lower $\lambda$ leads to a lower mean opinion score, as expected, though not to an intolerable degree.}
   \label{fig:TurkResults}

### 2022-11-15 writeup/paper.tex
Tweaking experiment figures

@@
 \begin{figure}
+  \begin{minipage}[c]{0.6\textwidth}
+    \caption{
+      Every crossing in a tour can be removed with a 2-opt swap to yield a tour of a smaller distance, since, by the triangle inequality, $d(X_i, X_j) + d(X_{i+1}, X_{j+1}) < (a+d) + (b+c) = d(X_i, X_{i+1}) + d(X_j, X_{j+1})$.
+This may introduce new crossings (shown in red), but these and other crossings will be resolved in future 2-opt swaps
+    } \label{fig:TwoOpt}
+  \end{minipage}
+  \begin{minipage}[c]{0.38\textwidth}
+    \includegraphics[width=\textwidth]{2Opt.pdf}
+  \end{minipage}\hfill
+
+\end{figure}
+
+\begin{figure}
   \centering
-  \includegraphics[width=0.5\columnwidth]{2Opt.pdf}
-  \caption{Every crossing in a tour can be removed with a 2-opt swap to yield a tour of a smaller distance, since, by the triangle inequality, $d(X_i, X_j) + d(X_{i+1}, X_{j+1}) < (a+d) + (b+c) = d(X_i, X_{i+1}) + d(X_j, X_{j+1})$.
-This may introduce new crossings (shown in red), but these and other crossings will be resolved in future 2-opt swaps.}
-  \label{fig:TwoOpt}
+
+  \caption{.}
+  \label{}
 \end{figure}

### 2022-11-16 writeup/paper.tex
Adding shifts experiment figure, commenting out algorithm description of Vornoi stippling

@@
 
-\begin{algorithm}
-  \caption{Modified Weighted Voronoi Stippling \cite{secord2002weighted}}
-  \begin{algorithmic}[1]
-    \Procedure{VoronoiStipple}{$G$, $N$, $b$, $\sigma$, $f$}
-    \Comment{Grayscale image $G$, $N$ target points, brightness threshold $b$, Canny edge scale $\sigma$, density factor $f$}
-    \State $W_{ij} \gets \min(I_{ij}, b)$
-    \State $W_{ij} \gets W_{ij} - \min(W)$
-    \State $W_{ij} \gets 1 - W_{ij} / \max(W)$
-    \State $C \gets \text{canny}_{\sigma}(I)$ \Comment{1 if on canny edge, 0 otherwise}
-    \State $W_{ij} \gets \max(W_{ij}, C_{ij})$
-    \State  Sample $N$ random points $X \in \mathbb{R}^{N \times 2}$ by density according to $W$
-    \For{$k = 1:10$} \Comment{Lloyd's relaxation iterations}
-        \State \begin{equation}
-          X_i \gets \frac{ \sum_{(i, j) \in A_i} W_{ij} * (i, j) }{\sum_{(i, j) \in A_i} W_{ij}}
-        \end{equation}
-        \Comment{Where $A_i$ is the Voronoi region for point $X_i$}
-    \EndFor \\
-    \State Remove top $N(1-f)$ points from $X$ with furthest distance to their nearest neighbors \\
-    \Return $X$
-    \EndProcedure
-  \end{algorithmic}
-  \label{alg:voronoistipple}
-\end{algorithm}
+% \begin{algorithm}
+%   \caption{Modified Weighted Voronoi Stippling \cite{secord2002weighted}}
+%   \begin{algorithmic}[1]
+%     \Procedure{VoronoiStipple}{$G$, $N$, $b$, $\sigma$, $f$}
+%     \Comment{Grayscale image $G$, $N$ target points, brightness threshold $b$, Canny edge scale $\sigma$, density factor $f$}
+%     \State $W_{ij} \gets \min(I_{ij}, b)$
+%     \State $W_{ij} \gets W_{ij} - \min(W)$
+%     \State $W_{ij} \gets 1 - W_{ij} / \max(W)$
+%     \State $C \gets \text{canny}_{\sigma}(I)$ \Comment{1 if on canny edge, 0 otherwise}
+%     \State $W_{ij} \gets \max(W_{ij}, C_{ij})$
+%     \State  Sample $N$ random points $X \in \mathbb{R}^{N \times 2}$ by density according to $W$
+%     \For{$k = 1:10$} \Comment{Lloyd's relaxation iterations}
+%         \State \begin{equation}
+%           X_i \gets \frac{ \sum_{(i, j) \in A_i} W_{ij} * (i, j) }{\sum_{(i, j) \in A_i} W_{ij}}
+%         \end{equation}
+%         \Comment{Where $A_i$ is the Voronoi region for point $X_i$}
+%     \EndFor \\
+%     \State Remove top $N(1-f)$ points from $X$ with furthest distance to their nearest neighbors \\
+%     \Return $X$
+%     \EndProcedure
+%   \end{algorithmic}
+%   \label{alg:voronoistipple}
+% \end{algorithm}
 
@@
 Figure~\ref{fig:caltech101examples}).
-Finally, we include the option to filter out points by density to clean up the stipple before the next step.
-Algorithm~\ref{alg:voronoistipple} provides more details.
+%Algorithm~\ref{alg:voronoistipple} provides more details.
 
@@
 
-\end{figure}
-
-\begin{figure}
-  \centering
-
-  \caption{.}
-  \label{}
 \end{figure}
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\columnwidth]{ShiftsExperiment.pdf}
+  \caption{}
+  \label{fig:ShiftsExperiment}
+\end{figure}
+
 \subsection{Subjective Listening Experiment}

### 2022-11-16 viewer/audio.js
Starting to generalize code to handle 3D

@@ -85,7 +85,7 @@ class SampledAudio {
         canvas.width=width;
         canvas.height=width;
         canvasArea.appendChild(canvas);
-        that.stegCanvas = new StegCanvas2D(canvas, that.audioPlayer, that.channels[0], that.sr, folder, params);
+        that.stegCanvas = new StegCanvas(canvas, that.audioPlayer, that.channels[0], that.sr, folder, params);
         resolve();
       });
     });

### 2022-11-16 viewer/main.js

@@ -11,4 +11,4 @@ tuneInput.addEventListener('change', function(e) {
     reader.readAsArrayBuffer(tuneInput.files[0]);
 });
 
-audio.loadFile("examples/usher-baby-2d.mp3", canvasArea);
+audio.loadFile("examples/usher-baby-2d-fac0.1.mp3", canvasArea);

### 2022-11-16 viewer/stegcanvas.js

@@ -21,6 +21,30 @@ void main() {
   v_color = a_color;
 }`;
 
+
+
+const VERT_SRC_3D = `
+attribute vec4 a_info;
+attribute vec3 a_color;
+
+// Uniforms set from Javascript that are constant
+// over all fragments
+uniform mat4 uMVMatrix; // Where the origin (0, 0) is on the canvas
+uniform mat4 uPMatrix;
+uniform float uPointSize; // Size to draw points
+
+varying float v_time;
+varying vec3 v_color;
+
+void main() {
+  gl_PointSize = uPointSize;
+  vec4 a_position = vec4(a_info.x, a_info.y, a_info.z, 1.0);
+  gl_Position = uPMatrix * uMVMatrix * a_position;
+  v_time = a_info.w;
+  v_color = a_color;
+}`;
+
+
 const FRAG_SRC = `
 precision highp float;
 
@@ -123,7 +147,7 @@ function getShaderProgramAsync(gl, prefix) {
     });
 }
 
-class StegCanvas2D {
+class StegCanvas {
     /**
      * 
      * @param {DOM Element} glcanvas Handle to GL Canvas
@@ -147,7 +171,7 @@ class StegCanvas2D {
         }
         this.centervec = [0, 0];
         this.scale = 1;
-        let defaultParams = {"win":1024, "L":16, "Q":4, "freq1":1, "freq2":2, "colormap":"Spectral"};
+        let defaultParams = {"win":1024, "L":16, "Q":4, "freq1":1, "freq2":2, "freq3":-1, "colormap":"Spectral"};
         for (let param in defaultParams) {
             if (param in params) {
                 this[param] = params[param];
@@ -164,7 +188,7 @@ class StegCanvas2D {
             glcanvas.gl.viewportHeight = glcanvas.height;
             this.glcanvas = glcanvas;
             this.setupMenus(folder, colormap);
-            this.loadShader();
+            this.loadShaders();
             this.setupMouseHandlers();
             this.extractSignal();
             const repaint = () => {requestAnimationFrame(that.render.bind(that));};
@@ -208,6 +232,7 @@ class StegCanvas2D {
         folder.add(this, "Q", 1, 10, 1).onChange(this.extractSignal.bind(this));
         folder.add(this, "freq1", 0, Math.floor(this.win/2), 1).onChange(this.extractSignal.bind(this));
         folder.add(this, "freq2", 0, Math.floor(this.win/2), 1).onChange(this.extractSignal.bind(this));
[…]

### 2022-11-16 viewer/dspworker.js
Adding capability to shift audio samples in GUI

@@ -1,6 +1,7 @@
 onmessage = function(event) {
     const samples = event.data.samples;
     const win = event.data.win;
+    const shift = event.data.shift;
     const L = event.data.L;
     const Q = event.data.Q;
     const freqs = event.data.freqs;
@@ -21,7 +22,7 @@ onmessage = function(event) {
 
     // Step 2: Compute spectrogram at chosen bins
     postMessage({"type":"newTask", "taskString":"Computing spectrogram"});
-    let M = Math.floor(samples.length/win);
+    let M = Math.floor((samples.length-shift)/win);
     let SM = []; // Magnitudes
     let SP = []; // Phases
     for (let i = 0; i < freqs.length; i++) {
@@ -31,8 +32,8 @@ onmessage = function(event) {
             let cosSum = 0;
             let sinSum = 0;
             for (let k = 0; k < win; k++) {
-                cosSum += samples[j*win+k]*cos[i][k];
-                sinSum += samples[j*win+k]*sin[i][k];
+                cosSum += samples[shift+j*win+k]*cos[i][k];
+                sinSum += samples[shift+j*win+k]*sin[i][k];
             }
             SMi[j] = Math.sqrt(cosSum*cosSum + sinSum*sinSum);
             SPi[j] = Math.atan2(sinSum, cosSum);

### 2022-11-16 viewer/stegcanvas.js

@@ -165,13 +165,16 @@ class StegCanvas {
         glcanvas.addEventListener("contextmenu", function(e){ e.stopPropagation(); e.preventDefault(); return false; }); //Need this to disable the menu that pops up on right clicking
         this.colorBuffers = {};
 
-        // Viewing options
+        // 2D Viewing options
+        this.centervec = [0, 0];
+        this.scale = 1;
+
+        // Decoder parameters
+        this.coords = [];
         if (params === undefined) {
             params = {};
         }
-        this.centervec = [0, 0];
-        this.scale = 1;
-        let defaultParams = {"win":1024, "L":16, "Q":4, "freq1":1, "freq2":2, "freq3":-1, "colormap":"Spectral"};
+        let defaultParams = {"win":1024, "shift":0, "L":16, "Q":4, "freq1":1, "freq2":2, "freq3":-1, "colormap":"Spectral"};
         for (let param in defaultParams) {
             if (param in params) {
                 this[param] = params[param];
@@ -227,7 +230,14 @@ class StegCanvas {
         this.progressBar = new ProgressBar();
         this.folder = folder;
         this.stippleSize = 0.2;
-        folder.add(this, "win", 0, this.sr, 1).onChange(this.extractSignal.bind(this));
+        this.winGUI = folder.add(this, "win", 0, this.sr, 1).onChange(this.extractSignal.bind(this));
+        this.shiftGUI = folder.add(this, "shift", 0, this.win, 1).listen().onChange(this.extractSignal.bind(this));
+        this.winGUI.onChange(
+            function(v) {
+                that.shiftGUI.max(v);
+                that.shift = 0;
+            }
+        );
         folder.add(this, "L", 0).onChange(this.extractSignal.bind(this));
         folder.add(this, "Q", 1, 10, 1).onChange(this.extractSignal.bind(this));
         folder.add(this, "freq1", 0, Math.floor(this.win/2), 1).onChange(this.extractSignal.bind(this));
@@ -299,7 +309,7 @@ class StegCanvas {
             if (this.freq3 > -1) {
                 freqs.push(this.freq3);
             }
-            let payload = {samples:that.audioSamples, win:that.win, L:that.L, Q:that.Q, freqs:freqs};
+            let payload = {samples:that.audioSamples, win:that.win, shift:that.shift, L:that.L, Q:that.Q, freqs:freqs};
             worker.postMessage(payload);
             worker.onmessage = function(event) {
                 if (event.data.type == "newTask") {
[…]

### 2022-11-16 viewer/stegcanvas.js
Just about finished 3D viewer

@@ -56,6 +56,9 @@ void main() {
     gl_FragColor = vec4(v_color, 1);
 }`;
 
+const mat4 = glMatrix.mat4;
+const vec3 = glMatrix.vec3;
+
 
 getMousePos = function(evt) {
     if ('touches' in evt) {
@@ -169,12 +172,18 @@ class StegCanvas {
         this.centervec = [0, 0];
         this.scale = 1;
 
+        // 3D Viewing options
+        this.mvMatrix = mat4.create();
+        this.pMatrix = mat4.create();
+        this.camera = new MousePolarCamera(glcanvas.width, glcanvas.height, 0.75);
+        this.farR = 2.0;
+
         // Decoder parameters
         this.coords = [];
         if (params === undefined) {
             params = {};
         }
-        let defaultParams = {"win":1024, "shift":0, "L":16, "Q":4, "freq1":1, "freq2":2, "freq3":-1, "colormap":"Spectral"};
+        let defaultParams = {"win":1024, "shift":0, "L":16, "Q":4, "freq1":1, "freq2":2, "freq3":3, "colormap":"Spectral"};
         for (let param in defaultParams) {
             if (param in params) {
                 this[param] = params[param];
@@ -281,8 +290,8 @@ class StegCanvas {
         // Step 2: Setup 3D Shader
         let shader3d = getShaderProgram(gl, "stipple", VERT_SRC_3D, FRAG_SRC);
         // Extract uniforms and store them in the shader object
-        shader3d.uCenterUniform = gl.getUniformLocation(shader3d, "uCenter");
-        shader3d.uScaleUniform = gl.getUniformLocation(shader3d, "uScale");
+        shader3d.uPMatrixUniform = gl.getUniformLocation(shader3d, "uPMatrix");
+        shader3d.uMVMatrixUniform = gl.getUniformLocation(shader3d, "uMVMatrix");
         shader3d.uTimeUniform = gl.getUniformLocation(shader3d, "uTime");
         shader3d.uPointSizeUniform = gl.getUniformLocation(shader3d, "uPointSize");
         // Extract the info buffer and store it in the shader object
@@ -398,11 +407,26 @@ class StegCanvas {
         gl.clearColor(1, 1, 1, 1.0);
         gl.clear(gl.COLOR_BUFFER_BIT);
 
-        let shader = this.shader2d;
-        gl.useProgram(shader);
         // Step 1: Setup uniform variables that are sent to the shaders
-        gl.uniform2fv(shader.uCenterUniform, this.centervec);
[…]

### 2022-11-16 viewer/stegcanvas.js
Adding centering on bounding box for 3D, and it works great!

@@ -176,14 +176,15 @@ class StegCanvas {
         this.mvMatrix = mat4.create();
         this.pMatrix = mat4.create();
         this.camera = new MousePolarCamera(glcanvas.width, glcanvas.height, 0.75);
-        this.farR = 2.0;
+        this.farR = 1.0;
+        this.bbox = [0, 1, 0, 1, 0, 1];
 
         // Decoder parameters
         this.coords = [];
         if (params === undefined) {
             params = {};
         }
-        let defaultParams = {"win":1024, "shift":0, "L":16, "Q":4, "freq1":1, "freq2":2, "freq3":3, "colormap":"Spectral"};
+        let defaultParams = {"win":1024, "shift":0, "L":16, "Q":4, "freq1":1, "freq2":2, "freq3":-1, "colormap":"Spectral"};
         for (let param in defaultParams) {
             if (param in params) {
                 this[param] = params[param];
@@ -368,12 +369,52 @@ class StegCanvas {
         gl.bindBuffer(gl.ARRAY_BUFFER, this.infoBuffer);
         gl.bufferData(gl.ARRAY_BUFFER, info, gl.STATIC_DRAW);
         let shader = this.shader2d;
-        if (dim > 2) {
+        if (dim > 3) {
             shader = this.shader3d;
+            this.centerOnBBox();
         }
         gl.vertexAttribPointer(shader.infoLocation, dim, gl.FLOAT, false, 0, 0);
         this.render();
     }
+
+    /**
+     * Center 3D camera on the bounding box of the curve
+     */
+    centerOnBBox() {
+        const coords = this.coords;
+        this.bbox = [coords[0][0], coords[0][0], 
+                     coords[1][0], coords[1][0],
+                     coords[2][0], coords[2][0]];
+        for (let i = 0; i < this.coords[0].length; i++) {
+            if (coords[0][i] < this.bbox[0]) {
+                this.bbox[0] = coords[0][i];
+            }
+            if (coords[0][i] > this.bbox[1]) {
+                this.bbox[1] = coords[0][i];
+            }
+            if (coords[1][i] < this.bbox[2]) {
+                this.bbox[2] = coords[1][i];
+            }
+            if (coords[1][i] > this.bbox[3]) {
+                this.bbox[3] = coords[1][i];
+            }
+            if (coords[2][i] < this.bbox[4]) {
+                this.bbox[4] = coords[2][i];
[…]

### 2022-11-17 writeup/paper.tex
Finished abstract, updating some figures

@@
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-15--250 words.
 
-\keywords{Steganography, Traveling Salesperson Art, Hidden Signals}
+  In this work, we create artistic closed loop curves that trace out images and 3D shapes, which we then hide in musical audio as a form of steganography.
+We use traveling salesperson art to create artistic plane loops to trace out image contours, and we use Hamiltonian cycles on triangle meshes to create artistic space loops that fill out 3D surfaces.
+Our embedding scheme is designed to faithfully preserve the geometry of these loops while keeping their presence undetectable to the audio listener.
+To accomplish this, we hide each dimension of the curve in a different frequency, and we perturb a regularized version of the magnitude of that frequency to best match the target curve at that dimension, while hiding scale information in that frequency's phase.
+In the process, we exploit geometric properties of the curves to help to more effectively hide and recover them.
+Our scheme is simple and encoding happens efficiently with a nonnegative least squares framework, while decoding is trivial.
+We validate our technique quantitatively on large datasets of images and audio, and we show results of a crowd sourced listening test that validate that the hidden information is indeed unobtrusive.
+
+\keywords{Steganography, Traveling Salesperson Art, Hamiltonian Cycles, Audio Processing, Hidden Signals}
 \end{abstract}
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{ShiftsExperiment.pdf}
+  \includegraphics[width=\columnwidth]{ShiftsExperiment.pdf}
   \caption{}

### 2022-11-17 writeup/paper.tex
Progress on literature review

@@
 We use traveling salesperson art to create artistic plane loops to trace out image contours, and we use Hamiltonian cycles on triangle meshes to create artistic space loops that fill out 3D surfaces.
-Our embedding scheme is designed to faithfully preserve the geometry of these loops while keeping their presence undetectable to the audio listener.
+Our embedding scheme is designed to faithfully preserve the geometry of these loops after lossy compression, while keeping their presence undetectable to the audio listener.
 To accomplish this, we hide each dimension of the curve in a different frequency, and we perturb a regularized version of the magnitude of that frequency to best match the target curve at that dimension, while hiding scale information in that frequency's phase.
@@
 
-Our goals and design constraints are as follows:
+Steganography is the process of hiding one data stream ``in plain sight'' within another data stream known as a ``carrier.''  In this work, we are interested in using audio as a carrier to store images, which has been relatively unexplored in the academic literature (Section~\ref{sec:priorwork}).
+As with any stegonographic technique, people can use this as a general means of covert communication, but it can also be used for artists to hide images and to watermark their tunes.
+One such example occurred when Aphex Twin embedded a face image inside the spectrogram of their ``Windowlicker'' song \cite{mathews2004music}, though the technique yields very loud, inharmonic, scratchy sounds.
+By contrast, we seek an embedding of the image that is undetectable.
+Like Aphex Twin, however, we would like the image to survive lossy audio compression so that people can communicate their images via social media, which makes the problem significantly more challenging.
+
+To make our audio steganography system as robust and usable as possible, we have the following design goals:
 \begin{enumerate}
     \item \label{goal:imperceptible} The hidden data should be audibly imperceptible
-    \item \label{goal:geomquality} The hidden data should be faithfully preserved and {\em robust to compression}
+    \item \label{goal:geomquality} The hidden data should be faithfully preserved and {\em robust to lossy compression}
     \item \label{goal:misalignment} The hidden data should be robust to frame misalignment, or it should be possible to recover a frame alignment without any prior information
@@
 Goals ~\ref{goal:imperceptible} and ~\ref{goal:geomquality} are at odds with each other, and satisfying them simultaneously is the biggest challenge of this work.
+We formulate an objective function in Section~\ref{sec:formulation} to trade off both of these goals.
 
-Pipeline is simple enough that we have very good intuition for how it's working, and we validate its performance in Section~\ref{sec:experiments}.
+Rather than storing images directly in audio, we constrain our problem to hiding artistic curves that trace out images (Section~\ref{sec:tspart}) or 3D surface shapes (Section~\ref{sec:hamiltonian}).
+We hide each dimension of our curve in a different frequency, and we use sliding window sums of the frequency magnitudes to smooth them in time, which makes them more robust to compression, as we show in Section~\ref{sec:experiments}.
+Furthermore, since we know that the curves only move by a small amount between adjacent samples in time, we can exploit this fact to recover from frame misalignments to satisfy Goal~\ref{goal:misalignment}, as explained in Section~\ref{sec:framealignments}.
+In the end, all of the hidden information needed to reconstruct the curves is stored in the magnitudes and phases of frequencies in the audio, so no metadata is needed (Goal~\ref{goal:metadata}).
+Finally, the information needed to recover individual curves samples is localized in time, so the curves can be partially decoded from partial audio (Goal~\ref{goal:partial}).
 
 \subsection{Prior Work in Audio Steganography}
+\label{sec:priorwork}
+
+Before we proceed to describing the techniques for constructing artistic curves (Section~\ref{sec:tspart}, Section~\ref{sec:hamiltonian}), and to ultimately hiding them in audio (Section~\ref{sec:methods}), we briefly review adjacent work in the area of audio steganography to put our work in context (for more information, review to these survey articles \cite{djebbar_comparative_2012, dutta_overview_2020}).
+
+As for most other steganographic carriers, the simplest techniques for audio steganography rely on changing the least significant bit of uncompressed encodings (e.g.
+\cite{cvejic_wavelet_2002}).
+Other early works rely on the ``frequency masking'' property of the human auditory system; that is, we don't hear frequencies if they are nearby to other frequencies of a larger magnitude.
+Binary data can be stored by controlling the relative amplitude of two frequencies that are masked in this way \cite{gopalan_unified_2009, gopalan2004audio}.
+Our technique for hiding dimensions on curves also changes amplitudes of tones in imperceptable ways.
+
+Beyond amplitude perturbations, it is also possible to keep the amplitudes fixed and to change the phases \cite{xiaoxiao_dong_data_2004, hwan_sik_yun_acoustic_2010}; the technique of \cite{malik_robust_2007} was particularly successful at this by manipulating the poles of allpass filters to encode binary data.
+One can also hide binary data by adding and manipulating echoes of a signal \cite{gruhl1996echo}, which is more robust than other techniques to lossy compression since it is akin to impulse responses of natural environments; however, the bit rate is quite low (on the order of dozens of bits per second).
+For another approach to compressed audio, some techniques are able to use the properties of mp3 files directly to hide information \cite{qiao_steganalysis_2009,atoum2013exploring}.
+Other techniques adapt wireless transmissions schemes, such as and on-off keying (OOK) \cite{madhavapeddy_audio_2005} (at a low bit rate of 8bps) and orthogonal frequency-division multiplexing (OFDM) \cite{eichelberger_receiving_2019} (at a higher bit rate of closer to 1kbps), to the audio domain.
+Some more recent techniques use deep learning \cite{kreuk2020hide, wu2020audio}
+
+Most of the hidden messages in the audio steganography literature are in binary format, but a few recent works have focused on hiding images specifically using deep learning \cite{cui_multi-stage_2021, geleta_pixinwav_2021, takahashi_source_2022}.
+We have a similar perspective that rather than attempting to extract binary sequences exactly, we can
 
 \section{Traveling Salesperson Art}
+\label{sec:tspart}
 
@@
 
-Traveling Salesperson (TSP) art \cite{bosch2004continuous, kaplan2005tsp,bosch2008connecting} is an automated artistic line drawing pipeline which computes a {\em simple closed loop} to approximate a source image.
+To devise 2D curves that stand in for images, we turn to the technique of  Traveling Salesperson (TSP) art \cite{bosch2004continuous, kaplan2005tsp,bosch2008connecting}, which is an automated artistic line drawing pipeline which computes a {\em simple closed loop} to approximate a source image.
 ``Simple'' in this context does not imply a lack of complexity; rather, it means that a curve does not intersect itself (see, for example, the Jordan Curve Theorem \cite{bosch2009jordan}).
@@
 \section{Curve Embedding in Audio}
+\label{sec:methods}
 
@@
 \subsection{Formulation of Least Squares Problem}
+\label{sec:formulation}
 
@@
 
-We use the technique presented by the authors of \cite{xiaoxiao_dong_data_2004} to recover the scales of each component.
+Since we intentionally rescale the dimensions of the target to match the dynamic range of each SW-STFT component, we lose the aspect ratio between the dimensions.
+But since we have only perturbed the magnitude components of the frequency indices $k_i$, we still have some freedom to perturb the phases to store additional information.
+To that end, we use the technique presented by the authors of \cite{xiaoxiao_dong_data_2004} to store the relative scale of each dimension.
 
 \subsection{Recovering Frame Alignments}
+\label{sec:framealignments}
 

### 2022-11-17 writeup/paper.tex
Finished background, and cutting some stuff to keep within the page limits

@@
 %
-\section{Introduction}
+\section{Introduction / Background}
 
@@
     \item \label{goal:imperceptible} The hidden data should be audibly imperceptible
-    \item \label{goal:geomquality} The hidden data should be faithfully preserved and {\em robust to lossy compression}
+    \item \label{goal:geomquality} The hidden data should be faithfully preserved {\em under lossy compression}
     \item \label{goal:misalignment} The hidden data should be robust to frame misalignment, or it should be possible to recover a frame alignment without any prior information
@@
 \cite{cvejic_wavelet_2002}).
-Other early works rely on the ``frequency masking'' property of the human auditory system; that is, we don't hear frequencies if they are nearby to other frequencies of a larger magnitude.
-Binary data can be stored by controlling the relative amplitude of two frequencies that are masked in this way \cite{gopalan_unified_2009, gopalan2004audio}.
-Our technique for hiding dimensions on curves also changes amplitudes of tones in imperceptable ways.
+Other early works rely on the ``frequency masking'' property of the human auditory system.
+Binary data is stored by controlling the relative amplitude of two frequencies that are masked in this way \cite{gopalan_unified_2009, gopalan2004audio}.
 
@@
 Other techniques adapt wireless transmissions schemes, such as and on-off keying (OOK) \cite{madhavapeddy_audio_2005} (at a low bit rate of 8bps) and orthogonal frequency-division multiplexing (OFDM) \cite{eichelberger_receiving_2019} (at a higher bit rate of closer to 1kbps), to the audio domain.
-Some more recent techniques use deep learning \cite{kreuk2020hide, wu2020audio}
 
-Most of the hidden messages in the audio steganography literature are in binary format, but a few recent works have focused on hiding images specifically using deep learning \cite{cui_multi-stage_2021, geleta_pixinwav_2021, takahashi_source_2022}.
-We have a similar perspective that rather than attempting to extract binary sequences exactly, we can
+Most of the hidden messages in the audio steganography literature are in binary format, but a few recent works have focused on hiding images pixels using deep learning to train networks to a ``hiding network'' and a ``reveal network'' to work in tandem ot encode an image in an audio stream and then to decode its addition into the carrier, respectively, while maximizing quality of the decoded image and the encoded audio \cite{cui_multi-stage_2021, geleta_pixinwav_2021, takahashi_source_2022, domenech2022hiding}.
+Not only do we also attempt to hide images, but we have a similar perspective that rather than attempting to extract binary sequences exactly, we can tolerate progressive noise in the reconstructions.
+Challenges of deep-learning based approaches include the need to extensively train on examples, the difficulty of including a loss term that can model the effect of lossy audio compression, and the difficulty of training to be robust to frame misalignment (Goal~\ref{goal:misalignment}).
+We sidestep these challenges in our work by using a simple model based on hiding in frequencies.
 
-\section{Traveling Salesperson Art}
+\subsection{Traveling Salesperson Art}
 \label{sec:tspart}
@@
 
-To devise 2D curves that stand in for images, we turn to the technique of  Traveling Salesperson (TSP) art \cite{bosch2004continuous, kaplan2005tsp,bosch2008connecting}, which is an automated artistic line drawing pipeline which computes a {\em simple closed loop} to approximate a source image.
+To devise 2D curves that stand in for images, we use Traveling Salesperson (TSP) art \cite{bosch2004continuous, kaplan2005tsp,bosch2008connecting}, which is an automated artistic line drawing pipeline which computes a {\em simple closed loop} to approximate a source image.
 ``Simple'' in this context does not imply a lack of complexity; rather, it means that a curve does not intersect itself (see, for example, the Jordan Curve Theorem \cite{bosch2009jordan}).
@@
 We follow the TSP Art technique of \cite{kaplan2005tsp}, with a few modifications, as described below.
-
-\subsection{Voronoi Stippling}
-\label{sec:stippling}
 
@@
 The first step in TSP art is to generate a stipple pattern $X$ to best approximate a grayscale image $G$.
-Following the authors of \cite{kaplan2005tsp}, we use Secord's technique for Voronoi stippling \cite{secord2002weighted}.
-This consists taking an initial sample of points according to some density weights $W$ and then repeatedly moving them closer the weighted centroid of their Voronoi regions (an instance of Lloyd's algorithm) so that they are spread more evenly and look less ``noisy.''  Secord \cite{secord2002weighted} takes the weight $W_{ij}$ at a pixel to be inversely proportional to its brightness, using a weight of $0$ above some brigtness threshold $b$.
+Following the authors of \cite{kaplan2005tsp}, we use Secord's technique for Voronoi stippling \cite{secord2002weighted}, which takes an initial sample of points according to some density weights $W$ and then repeatedly moves them closer the weighted centroid of their Voronoi regions (an instance of Lloyd's algorithm) so that they are spread more evenly.
+Secord \cite{secord2002weighted} takes the weight $W_{ij}$ at a pixel to be inversely proportional to its brightness, using a weight of $0$ above some brigtness threshold $b$.
 This leads more dots to concentrate in darker regions; however, the algorithm may fail to sample any dots along important edges between brighter regions (the authors of \cite{li2011structure} also observed this).
-To ameliorate this, we run a Canny edge detector \cite{canny1986computational} on the original image and set the weight of any pixels along an edge to be 1, so that the final weights promote samples both in darker regions and along edges of any kind.
-This addition is particularly helpful for line drawings, including images with text (e.g.
-Figure~\ref{fig:caltech101examples}).
+To mitigate this, we run a Canny edge detector \cite{canny1986computational} on the original image and set the weight of any pixels along an edge to be 1, so that the final weights promote samples both in darker regions and along edges of any kind.
+This addition is particularly helpful for line drawings.
 %Algorithm~\ref{alg:voronoistipple} provides more details.
 
-\subsection{Traveling Salesperson Tours}
-\label{sec:tsp}
 Once a stipple has been established, the next step in TSP art is to ``connect the dots'' with a closed loop that visits each stipple point exactly once, referred to as a ``tour''\footnote{A loop with these properties is otherwise known as a {\em Hamiltonian cycle} on a complete graph over the points}.
@@
 
-\begin{figure}
-  \begin{minipage}[c]{0.6\textwidth}
-    \caption{
-      Every crossing in a tour can be removed with a 2-opt swap to yield a tour of a smaller distance, since, by the triangle inequality, $d(X_i, X_j) + d(X_{i+1}, X_{j+1}) < (a+d) + (b+c) = d(X_i, X_{i+1}) + d(X_j, X_{j+1})$.
+% \begin{figure}
+%   \begin{minipage}[c]{0.6\textwidth}
+%     \caption{
+%       Every crossing in a tour can be removed with a 2-opt swap to yield a tour of a smaller distance, since, by the triangle inequality, $d(X_i, X_j) + d(X_{i+1}, X_{j+1}) < (a+d) + (b+c) = d(X_i, X_{i+1}) + d(X_j, X_{j+1})$.
 This may introduce new crossings (shown in red), but these and other crossings will be resolved in future 2-opt swaps
-    } \label{fig:TwoOpt}
-  \end{minipage}
-  \begin{minipage}[c]{0.38\textwidth}
-    \includegraphics[width=\textwidth]{2Opt.pdf}
-  \end{minipage}\hfill
+%     } \label{fig:TwoOpt}
+%   \end{minipage}
+%   \begin{minipage}[c]{0.38\textwidth}
+%     \includegraphics[width=\textwidth]{2Opt.pdf}
+%   \end{minipage}\hfill
 
-\end{figure}
+% \end{figure}
 
@@
 We repeat this step as long as such a swap is still possible.
-Though this is not guaranteed to yield an optimal TSP tour, it does produce tours which are simple; that is, every crossing is removed (Figure~\ref{fig:TwoOpt}).
+Though this is not guaranteed to yield an optimal TSP tour, it does produce tours which are simple; that is, every crossing is removed.% (Figure~\ref{fig:TwoOpt}).
 
-\subsection{Curvature Shortening Flow}
+\subsubsection{Curvature Shortening Flow}
 
 \begin{figure}
-  \centering
+  \begin{minipage}[c]{0.4\textwidth}
+    \caption{
+      Anticipating that mp3 compression will introduce noise to our embedded curves, we pre-smooth them before hiding them using one iteration of curvature-shortening flow at $\sigma=1$, which smooths the curves without introducing any crossings.
+    } \label{fig:CurvatureShortening}
+  \end{minipage}
+  \begin{minipage}[c]{0.6\textwidth}
     \includegraphics[width=\columnwidth]{CurvatureShortening.png}
-  \caption{Anticipating that mp3 compression will introduce noise to our embedded curves, we pre-smooth them before hiding them using one iteration of curvature-shortening flow, which smooths the curves without introducing any crossings.
-We find $\sigma=1$ to be a good tradeoff between smoothness and detail.}
-  \label{fig:CurvatureShortening}
+  \end{minipage}\hfill
+
 \end{figure}
+
+% In particular, let 
+% \begin{equation}
+%   g_{\sigma}[j] = c_1 e^{-j^2 / (2 \sigma^2)}, 
+%   g'_{\sigma}[j] = - c_2 \frac{j}{\sigma^2} e^{-j^2 / (2 \sigma^2)}
+% \end{equation}
+
+% where $c_1$ and $c_2$ are appropriate normalization constants.  Then we estimate the arc length of a sampled curve $\gamma[j]$ with the rectangular integral of a smoothed velocity estimate:
+
+% \begin{equation}
+%   \label{eq:arclen}
+%   s_{\sigma}[j] = \sum_{k=1}^j |(\gamma * g'_{\sigma})[k]|
+% \end{equation}
 
@@
 The technique works by numerically by convolving coordinates of each curve with smoothed versions of Gaussians and their derivatives.
-In particular, let
-\begin{equation}
-  g_{\sigma}[j] = c_1 e^{-j^2 / (2 \sigma^2)}, 
-  g'_{\sigma}[j] = - c_2 \frac{j}{\sigma^2} e^{-j^2 / (2 \sigma^2)}
-\end{equation}
 
-where $c_1$ and $c_2$ are appropriate normalization constants.  Then we estimate the arc length of a sampled curve $\gamma[j]$ with the rectangular integral of a smoothed velocity estimate:
-
-\begin{equation}
-  \label{eq:arclen}
-  s_{\sigma}[j] = \sum_{k=1}^j |(\gamma * g'_{\sigma})[k]|
-\end{equation}
-
-To approximately smooth a curve via one step of curvature-shortening flow, Mokhtarian and Mackworth \cite{mokhtarian1992theory} show that it suffices to first re-parameterize by the arc length $s_{\sigma}$ in Equation~\ref{eq:arclen}, and then to smooth the curve by convolving with $g_{\sigma}$.
-The beauty of convolving with Gaussians as such is that $\gamma$ does not even have to be differentiable, so this works on our piecewise linear TSP tours.
-Furthermore, by the Gage-Hamilton-Grayson theorem, simple curves that undergo curvature shortening flow {\em remain simple} and eventually become convex, shrinking to a point under repeated applications of the flow.
+To approximately smooth a curve via one step of curvature-shortening flow, Mokhtarian and Mackworth \cite{mokhtarian1992theory} show that it suffices to first re-parameterize by the arc length, and then to smooth the curve by convolving with once with a Gaussian\footnote{The beauty of convolving with Gaussians as such is that $\gamma$ does not even have to be differentiable, so this works on our piecewise linear TSP tours.}.
+By the Gage-Hamilton-Grayson theorem, simple curves that undergo curvature shortening flow {\em remain simple} and eventually become convex, shrinking to a point under repeated applications of the flow.
 Figure~\ref{fig:CurvatureShortening} shows an example of one application of curvature shortening flow for different $\sigma$ values.
 
-\section{Hamiltonian Paths on Watertight Triangle Meshes}
+\subsection{Hamiltonian Paths on Watertight Triangle Meshes}
 \label{sec:hamiltonian}
@@
 
-We now introduce our new algorithm for hiding artistic space curves, such as 2D TSP paths (Section~\ref{sec:tsp}) and 3D Hamiltonian paths (Section~\ref{sec:hamiltonian}), in audio.
+We now introduce our new algorithm for hiding artistic space curves in audio.
 Before we go into the details, we first define quantitative measurements for measuring the fit to the original audio (Goal~\ref{goal:imperceptible}) and the geometric quality of the hidden curve (Goal~\ref{goal:geomquality}).
@@
 For our geometric measurement of quality, let $X_i$ be a sequence of $M$ target curve points in $\mathbb{R}^d$ and $Y_i$ be a sequence of $M$ reconstructed points in $\mathbb{R}^d$.
-Then we define the {\em mean geometric distortion} is simply as the mean Euclidean distance between these points
-
-\begin{equation}
-  \label{eq:distortion}
-  \text{distortion}(Y|X) = \frac{1}{M} \sum_{j=1}^M ||X_j - Y_j||_2
-\end{equation}
+Then we define the {\em mean geometric distortion} is simply as the mean Euclidean distance between these points: $\text{distortion}(Y|X) = \frac{1}{M} \sum_{j=1}^M ||X_j - Y_j||_2$.
 
@@
   \centering
-  \includegraphics[width=\columnwidth]{WindowEffect.pdf}
-  \caption{This figure shows the effect of varying $\ell$ for a fixed $\lambda=0.1$, using the lowest two non-DC frequencies to embed each coordinate.
+  \includegraphics[width=0.8\columnwidth]{WindowEffect.pdf}
+  \caption{Varying $\ell$ for a fixed $\lambda=0.1$, using the lowest two non-DC frequencies to carry.
 A larger $\ell$ for the SW-STFT in Equation~\ref{eq:objfn} leads to smoother curves which are more likely to survive compression, but an $\ell$ that's too large may over-smooth.}
@@
   \centering
-  \includegraphics[width=\columnwidth]{LambdaEffect.pdf}
-  \caption{This figure shows the effect of varying $\lambda$ for a fixed $\ell=16$, embedding using the lowest two non-DC frequencies to.
+  \includegraphics[width=0.8\columnwidth]{LambdaEffect.pdf}
+  \caption{Varying $\lambda$ for a fixed $\ell=16$.
 A smaller $\lambda$ in Equation~\ref{eq:objfn} leads to higher geometric fidelity (Goal~\ref{goal:geomquality}), at the cost of audio quality (Goal~\ref{goal:imperceptible}), as measured by SNR.}

### 2022-11-17 writeup/paper.tex
Finished writing quantitative experiments

@@
 By contrast, we seek an embedding of the image that is undetectable.
-Like Aphex Twin, however, we would like the image to survive lossy audio compression so that people can communicate their images via social media, which makes the problem significantly more challenging.
+Like Aphex Twin, however, {\em we would like the image to survive lossy audio compression} so that people can communicate their images via social media, which makes the problem significantly more challenging.
 
@@
     \item \label{goal:misalignment} The hidden data should be robust to frame misalignment, or it should be possible to recover a frame alignment without any prior information
-    \item \label{goal:metadata} No metadata should be required to retrieve the hidden data; (compressed) audio alone should suffice
+    \item \label{goal:metadata} No metadata should be required to retrieve the hidden data; (lossily compressed) audio alone should suffice
     \item \label{goal:partial} It should be possible to recover the data partially from partial audio chunks; that is, we don't need to wait for the entire data stream to recover the signal
@@
 
-Beyond amplitude perturbations, it is also possible to keep the amplitudes fixed and to change the phases \cite{xiaoxiao_dong_data_2004, hwan_sik_yun_acoustic_2010}; the technique of \cite{malik_robust_2007} was particularly successful at this by manipulating the poles of allpass filters to encode binary data.
+Beyond amplitude perturbations, it is also possible to keep the amplitudes fixed and to change the phases \cite{xiaoxiao_dong_data_2004, yun2009acoustic}; the technique of \cite{malik_robust_2007} was particularly successful at this by manipulating the poles of allpass filters to encode binary data.
 One can also hide binary data by adding and manipulating echoes of a signal \cite{gruhl1996echo}, which is more robust than other techniques to lossy compression since it is akin to impulse responses of natural environments; however, the bit rate is quite low (on the order of dozens of bits per second).
@@
 
-Most of the hidden messages in the audio steganography literature are in binary format, but a few recent works have focused on hiding images pixels using deep learning to train networks to a ``hiding network'' and a ``reveal network'' to work in tandem ot encode an image in an audio stream and then to decode its addition into the carrier, respectively, while maximizing quality of the decoded image and the encoded audio \cite{cui_multi-stage_2021, geleta_pixinwav_2021, takahashi_source_2022, domenech2022hiding}.
+Most of the hidden messages in the audio steganography literature are in binary format, but a few recent works have focused on hiding images pixels using deep learning to train a ``hiding network'' and a ``reveal network'' in tandem to encode an image in an audio stream and then to decode its addition into the carrier, respectively, while maximizing quality of the decoded image and the encoded audio \cite{cui_multi-stage_2021, geleta_pixinwav_2021, takahashi_source_2022, domenech2022hiding}.
 Not only do we also attempt to hide images, but we have a similar perspective that rather than attempting to extract binary sequences exactly, we can tolerate progressive noise in the reconstructions.
@@
 \label{sec:tspart}
-
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{TSPTour.pdf}
-  \caption{Our modified pipeline for creating TSP art.  Color on the tour indicates phase along the loop.}
-  \label{fig:TSPTour}
-\end{figure}
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{TSPTour.pdf}
+  \caption{Our modified pipeline for creating TSP art.  Color on the tour indicates phase along the loop.}
+  \label{fig:TSPTour}
+\end{figure}
+
+\begin{figure}
+  \begin{minipage}[c]{0.4\textwidth}
+    \caption{
+      Since mp3 compression introduces noise to our embedded curves, we pre-smooth them using one iteration of curvature-shortening flow at $\sigma=1$, which smooths the curves without introducing any crossings.
+    } \label{fig:CurvatureShortening}
+  \end{minipage}
+  \begin{minipage}[c]{0.6\textwidth}
+    \includegraphics[width=\columnwidth]{CurvatureShortening.png}
+  \end{minipage}\hfill
+\end{figure}
+
 The first step in TSP art is to generate a stipple pattern $X$ to best approximate a grayscale image $G$.
@@
 
-Once a stipple has been established, the next step in TSP art is to ``connect the dots'' with a closed loop that visits each stipple point exactly once, referred to as a ``tour''\footnote{A loop with these properties is otherwise known as a {\em Hamiltonian cycle} on a complete graph over the points}.
+Once a stipple has been established, the next step in TSP art is to ``connect the dots'' with a closed loop that visits each stipple point exactly once, referred to as a ``tour''.
 A well known objective function for a tour that doesn't ``jump too much'' is the total distance traveled, or the sum of all edge lengths, and a tour that achieves the optimum is known as a {\em traveling salesperson (TSP) tour}.
@@
 
-\begin{figure}
-  \begin{minipage}[c]{0.4\textwidth}
-    \caption{
-      Anticipating that mp3 compression will introduce noise to our embedded curves, we pre-smooth them before hiding them using one iteration of curvature-shortening flow at $\sigma=1$, which smooths the curves without introducing any crossings.
-    } \label{fig:CurvatureShortening}
-  \end{minipage}
-  \begin{minipage}[c]{0.6\textwidth}
-    \includegraphics[width=\columnwidth]{CurvatureShortening.png}
-  \end{minipage}\hfill
-
-\end{figure}
-
 % In particular, let 
@@
 
-\subsection{Hamiltonian Paths on Watertight Triangle Meshes}
+\subsection{Hamiltonian Cycles on Watertight Triangle Meshes}
 \label{sec:hamiltonian}
@@
   \centering
-  \includegraphics[width=\columnwidth]{HamiltonianHorse.pdf}
+  \includegraphics[width=0.8\columnwidth]{HamiltonianHorse.pdf}
   \caption{An example of the algorithm of Gopi and Epstein \cite{gopi2004single} on a horse model from the Princeton mesh segmentation benchmark \cite{Chen:2009:ABF}.}
@@
 
-In addition to 2D TSP tours on stipple patterns on planar images, we also create artistic 3D space curves that fill out the surfaces of 3D shapes following the technique of Gopi and Epstein \cite{gopi2004single}.
+In addition to 2D TSP tours on stipple patterns on planar images, we also create artistic 3D space loops that fill out the surfaces of 3D shapes following the technique of Gopi and Epstein \cite{gopi2004single}.
 They observe that watertight triangle meshes (those with no boundary) have a dual graph in which a perfect matching exists.
@@
 For our geometric measurement of quality, let $X_i$ be a sequence of $M$ target curve points in $\mathbb{R}^d$ and $Y_i$ be a sequence of $M$ reconstructed points in $\mathbb{R}^d$.
-Then we define the {\em mean geometric distortion} is simply as the mean Euclidean distance between these points: $\text{distortion}(Y|X) = \frac{1}{M} \sum_{j=1}^M ||X_j - Y_j||_2$.
+Then we define the {\em mean geometric distortion} is simply as the mean Euclidean distance between these points:
+\begin{equation}
+  \label{eq:distortion}
+  \text{distortion}(Y|X) = \frac{1}{M} \sum_{j=1}^M ||X_j - Y_j||_2
+\end{equation}
 
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{WindowEffect.pdf}
+  \includegraphics[width=0.9\columnwidth]{WindowEffect.pdf}
   \caption{Varying $\ell$ for a fixed $\lambda=0.1$, using the lowest two non-DC frequencies to carry.
@@
   \centering
-  \includegraphics[width=0.8\columnwidth]{LambdaEffect.pdf}
+  \includegraphics[width=0.9\columnwidth]{LambdaEffect.pdf}
   \caption{Varying $\lambda$ for a fixed $\ell=16$.
@@
 
-For a fixed $K$, we use the Viterbi algorithm to obtain a $\Theta$ minimizing Equation~\ref{eq:viterbiobj} in $O(MNK)$ time.
-Our use of the Viterbi algorithm for re-parameterizing geometric sequences is similar to the technique for corpus-based concatenative synthesis presented by the authors of \cite{schwarz2007corpus}.
-Algorithm~\ref{alg:viterbiwarp} gives more details.
+For a fixed $K$, we use the Viterbi algorithm to obtain a $\Theta$ minimizing Equation~\ref{eq:viterbiobj} in $O(MNK)$ time.  Algorithm~\ref{alg:viterbiwarp} gives more details.
 
@@
 But since we have only perturbed the magnitude components of the frequency indices $k_i$, we still have some freedom to perturb the phases to store additional information.
-To that end, we use the technique presented by the authors of \cite{xiaoxiao_dong_data_2004} to store the relative scale of each dimension.
+To that end, we use the technique presented by the authors of \cite{xiaoxiao_dong_data_2004} to store the relative scale of each dimension in the phase.
+We store the same scale in the phase of every STFT frame, and we take the median scales upon decoding.
 
@@
 \label{sec:framealignments}
+
+What we've described so far works for audio that is aligned to each window, but additional work needs to be done to address Goal ~\ref{goal:misalignment} if the audio to decode comes in misaligned.
+To this end, we use the fact that the hidden curves move only slightly between adjacent samples; a TSP tour is defined as length-minimizing, and adjacent samples in Hamiltonian cycles on meshes move only between neighboring triangles on the original mesh.
+If the embedding is frame aligned, the length of the curve should be minimized.
+Conversely, if the embedding is not frame aligned, the curve becomes noisy and is more likely to jump around quickly from sample to sample.
+Therefore, we can pick the alignment which minimizes the length in all possible shifts from $0$ to the STFT window length.
+Figure~\ref{fig:FrameAlignments} shows an example.
+We will empirically evaluate this in Section~\ref{sec:experiments}.
 
@@
   \caption{A shift which minimizes curve length is most likely the shift needed to re-align audio to frame windows.
-The dot here indicates the ground truth shift of an embedding using the lowest two non-DC frequencies with $\lambda=0.1, \ell=16$, and the global mins exactly match ground truth.}
+In this example with the embedding using the lowest two non-DC frequencies with $\lambda=0.1, \ell=16$, the global mins exactly match ground truth.}
   \label{fig:FrameAlignments}
 \end{figure}
-
-What we've described so far works for audio that is aligned to each window, but additional work needs to be done to address Goal ~\ref{goal:misalignment} if the audio to decode comes in misaligned.
-To this end, we use the fact that the hidden curves move only slightly between adjacent samples; a TSP tour is defined as length-minimizing, and adjacent samples in Hamiltonian cycles on meshes move only between neighboring triangles on the original mesh.
-If the embedding is frame aligned, the length of the curve should be minimized.
-Conversely, if the embedding is not frame aligned, the curve becomes noisy and is more likely to jump around quickly from sample to sample.
-Therefore, we can pick the alignment which minimizes the length in all possible shifts from $0$ to $win$.
-Figure~\ref{fig:FrameAlignments} shows an example.
-We will empirically evaluate this in Section~\ref{sec:experiments}.
 
@@
 
-Below we assess the performance of our system on an extensive set of tests
-
-Show caltech-101 and meshseg examples
-
 \begin{figure}
@@
   \includegraphics[width=\columnwidth]{caltech101_samples.png}
-  \caption{Examples of some TSP art on the Caltech-101 dataset \cite{li_andreeto_ranzato_perona_2022}.}
+  \caption{Examples of TSP art on the Caltech-101 dataset \cite{li_andreeto_ranzato_perona_2022}.}
   \label{fig:caltech101examples}
@@
   \includegraphics[width=\columnwidth]{MeshSegExamples.png}
-  \caption{Examples of some Hamiltonian cycles on triangle meshes from the Princeton mesh segmentation benchmark \cite{Chen:2009:ABF}.}
+  \caption{Examples of Hamiltonian cycles on triangle meshes from the Princeton mesh segmentation benchmark \cite{Chen:2009:ABF}.}
   \label{fig:meshsegexamples}
@@
 
-\subsection{Quantitative Results}
+We now quantitatively assess the performance of our system.
+To generate a large set of curves, we generate TSP art on the roughly 10,000 images in the Caltech-101 dataset  \cite{li_andreeto_ranzato_perona_2022} (e.g.
+Figure~\ref{fig:caltech101examples}), and we generate Hamiltonian cycles on the 380 watertight triangle meshes in the Princeton mesh segmentation database \cite{Chen:2009:ABF} (e.g.
+Figure~\ref{fig:meshsegexamples}).
+We then use the 1000 30 second audio clips from the Tzanetakis genre dataset \cite{tzanetakis2002musical} as carrier audio.
+For the Caltech-101 database, we partition the images into sets of 10, which are each encoded in one of the audio carriers varying $\lambda$ and $\ell$.
+Likewise, for the mesh segmentation dataset, we hide each Hamiltonian path in three different audio clips from the Tzanetakis dataset.
+In all cases, we encode the audio using lossy mp3 compression at 64 kbps.
 
@@
 As Figure~\ref{fig:ResultsFixedLam} shows, increasing the window length has a positive effect on geometric distortion, while moderate window lengths lead to the best SNR.
+Also, as expected, increasing $\lambda$ increases the SNR while leading to higher distortion, as shown in Figure~\ref{fig:ResultsFixedWin}.
+We also see a positive effect of the Viterbi alignment from Section~\ref{sec:reparam} on the SNR in Figure~\ref{fig:ResultsViterbiExperiment}.
+Finally, we run an experiment on the Caltech-101 dataset by choosing 4 random frame offsets per embedding, and we see in Figure~\ref{fig:ShiftsExperiment} that the algorithm of Section~\ref{sec:framealignments} recovers alignments well.
 
@@
   \includegraphics[width=\columnwidth]{ShiftsExperiment.pdf}
-  \caption{}
+  \caption{Estimating the frame alignment by minimizing the length (Section~\ref{sec:framealignments}) works nearly as well as perfect knowledge of the alignment.
+93\% of the shifts are within 10 of the ground truth for an STFT window length of 1024, which has hardly any effect on the geometry of the curve.}
   \label{fig:ShiftsExperiment}
@@
 
-\subsection{Subjective Listening Experiment}
+\subsubsection{Subjective Listening Experiment}
 
 \begin{figure}
-  \centering
-  \includegraphics[width=0.8\columnwidth]{Turk.pdf}
-  \caption{Results of the listening experiment on the Amazon Mechanical Turk.  A lower $\lambda$ leads to a lower mean opinion score, as expected, though not to an intolerable degree.}
-  \label{fig:TurkResults}
+  \begin{minipage}[c]{0.36\textwidth}
+    \caption{
+      Results of the listening experiment on the Amazon Mechanical Turk.  A lower $\lambda$ leads to a lower mean opinion score, as expected, though not to an intolerable degree.
+    } \label{fig:TurkResults}
+  \end{minipage}
+  \begin{minipage}[c]{0.64\textwidth}
+    \includegraphics[width=\columnwidth]{Turk.pdf}
+  \end{minipage}\hfill
+
 \end{figure}
 
-We can actually get higher SNRs using frequencies that are more audible
+Though the experiments above are encouraging, SNR can be misleading; frequencies that are more audible may actually have a higher SNR.
 
@@
 
+We have presented a model-based scheme for hiding artistic curves in audio, and the curves survive lossy compression.
 Talk about how this scheme works for any orthogonal decomposition of the signal and how we tried wavelets

### 2022-11-17 writeup/paper.tex
Adding two more 3D examples

@@
 To that end, we use the technique presented by the authors of \cite{xiaoxiao_dong_data_2004} to store the relative scale of each dimension in the phase.
-We store the same scale in the phase of every STFT frame, and we take the median scales upon decoding.
+We store the same scale in the phase of every STFT frame, and we take the scale to be the median of the phases upon decoding.
 
@@
   \centering
-  \includegraphics[width=\columnwidth]{CaltechGTzanFixedLam.pdf}
-  \includegraphics[width=\columnwidth]{MeshSegGTzanFixedLam.pdf}
-  \caption{The results embedding curves into clips from the Tzanetakis genre dataset varying the window length $\ell$ for a fixed $\lambda$.
-Moderate window lengths are the best choices for both SNR and distortion.
-We recommend $\ell=16$.}
-  \label{fig:ResultsFixedLam}
-\end{figure}
-
-\begin{figure}
-  \centering
   \includegraphics[width=\columnwidth]{CaltechGTzanFixedWin.pdf}
@@
   \centering
+  \includegraphics[width=\columnwidth]{CaltechGTzanFixedLam.pdf}
+  %\includegraphics[width=0.9\columnwidth]{MeshSegGTzanFixedLam.pdf}
+  \caption{Embedding curves into clips from the Tzanetakis genre dataset varying the window length $\ell$ for a fixed $\lambda$.
+Moderate window lengths are the best choices for both SNR and distortion.
+We recommend $\ell=16$.
+(3D is similar; see supplementary)}
+  \label{fig:ResultsFixedLam}
+\end{figure}
+
+Overall, we see slightly higher distortions and lower SNRs for 3D embeddings than 2D embeddings, which makes sense since there is one additional coordinate to hide.
+As expected, increasing $\lambda$ increases both the SNR and distortion, as shown in Figure~\ref{fig:ResultsFixedWin}.
+Also, as Figure~\ref{fig:ResultsFixedLam} shows, increasing the window length has a positive effect on geometric distortion, while moderate window lengths lead to the best SNR.
+We also see a positive effect of the Viterbi alignment from Section~\ref{sec:reparam} on the SNR in Figure~\ref{fig:ResultsViterbiExperiment}.
+Finally, we run an experiment on the Caltech-101 dataset by choosing 4 random frame offsets per embedding, and we see in Figure~\ref{fig:ShiftsExperiment} that the algorithm of Section~\ref{sec:framealignments} recovers alignments well.
+
+\begin{figure}
+  \centering
   \includegraphics[width=\columnwidth]{CaltechGTzanViterbiExperiment.pdf}
@@
 
-As Figure~\ref{fig:ResultsFixedLam} shows, increasing the window length has a positive effect on geometric distortion, while moderate window lengths lead to the best SNR.
-Also, as expected, increasing $\lambda$ increases the SNR while leading to higher distortion, as shown in Figure~\ref{fig:ResultsFixedWin}.
-We also see a positive effect of the Viterbi alignment from Section~\ref{sec:reparam} on the SNR in Figure~\ref{fig:ResultsViterbiExperiment}.
-Finally, we run an experiment on the Caltech-101 dataset by choosing 4 random frame offsets per embedding, and we see in Figure~\ref{fig:ShiftsExperiment} that the algorithm of Section~\ref{sec:framealignments} recovers alignments well.
-
 \begin{figure}
@@
   \caption{Estimating the frame alignment by minimizing the length (Section~\ref{sec:framealignments}) works nearly as well as perfect knowledge of the alignment.
-93\% of the shifts are within 10 of the ground truth for an STFT window length of 1024, which has hardly any effect on the geometry of the curve.}
+Using $\lambda=0.1, \ell=10$ over all images in Caltech-101, 93\% of the shifts are within 10 of the ground truth for an STFT window length of 1024, which has hardly any effect on the geometry of the curve.}
   \label{fig:ShiftsExperiment}
@@
 \subsubsection{Subjective Listening Experiment}
+
+Though the experiments above are encouraging, SNR can be misleading; frequencies that are more audible may actually have a higher SNR.
+To address this, we performed a crowd-sourced listening experiment on the Amazon Mechanical Turk where we embedded a random image from the Caltech-101 dataset in each of the Tzanetakis clips.
+We split them into 4 groups with no embedding (control), and with $\lambda = 0.1, 1, 10$, and we asked the listeners to rate the quality of the noise on the 5 point impairment scale of \cite{bassia2001robust} (5: imperceptible, 4: perceptible but not annoying, 3: slightly annoying, 2: annoying, 1: very annoying).
+In our experiment, we had 46 unique Turkers, 21 of whom participated in at least 40 rankings.
+Figure~\ref{fig:TurkResults} shows the results.
+Mean opinion scores (MOS) are correlated with $\lambda$, but there's not much of a difference between $\lambda=0.1$ and $\lambda=1$, which suggests using the former as a rule of thumb due to its lower geometric distortion.
+% We see a Pearson correlation of $r=0.48$ between the mean opinion score and the SNR in dB.
 
@@
 
-Though the experiments above are encouraging, SNR can be misleading; frequencies that are more audible may actually have a higher SNR.
+\section{Discussion / Conclusion}
 
-We ask questions similar to the authors of \cite{bassia2001robust}.
-
-46 unique Turkers, 21 of whom participated in at least 40 rankings.
-
-Figure~\ref{fig:TurkResults} shows the results.
-Mean opinion scores are correlated with $\lambda$, but there's not much of a difference between $\lambda=0.1$ and $\lambda=1$, which suggests using the former as a rule of thumb due to its lower geometric distortion.
-
-\section{Discussion}
-
-We have presented a model-based scheme for hiding artistic curves in audio, and the curves survive lossy compression.
-Talk about how this scheme works for any orthogonal decomposition of the signal and how we tried wavelets
+We have presented a model-based scheme for hiding artistic curves in audio, and the curves survive lossy compression while remaining reasonably imperceptible, as validated both with quantitative measurements and by humans.
+We hide the dimensions of curves in time regularized magnitudes of STFT frequencies, though coefficients of any orthogonal decomposition could work (we also implemented wavelets, though we found them more audibly perceptible).
+Our scheme is incredibly simple and requires no training.
+Decoding is nearly instantaneous, as it only requires computing the STFT of a few frequencies.
 

### 2022-11-17 src/stego.py
More examples!

@@ -374,6 +374,8 @@ class StegoSolver:
                 a = np.std(signal)/np.std(target[path])
                 b = np.mean(signal-a*self.targets[i][path])
                 self.targets[i] = a*self.targets[i] + b
+                if np.min(self.targets[i]) < 0:
+                    self.targets[i] -= np.min(self.targets[i])
                 diff += np.sum((target[path]-signal)**2)
             #print("Diff Before Viterbi", diff)
         if do_viterbi:
@@ -388,6 +390,8 @@ class StegoSolver:
                     a = np.std(signal)/np.std(target[path])
                     b = np.mean(signal-a*self.targets[i][path])
                     self.targets[i] = a*self.targets[i] + b
+                    if np.min(self.targets[i]) < 0:
+                        self.targets[i] -= np.min(self.targets[i])
                     diff += np.sum((target[path]-signal)**2)
                 #print("Diff After Viterbi", diff)
         if len(path) > 0:

### 2022-11-17 writeup/paper.tex
Finished papergit add -u!

@@
 
-As for most other steganographic carriers, the simplest techniques for audio steganography rely on changing the least significant bit of uncompressed encodings (e.g.
+As is the case for most other steganographic carriers, the simplest techniques for audio steganography rely on changing the least significant bit of uncompressed encodings (e.g.
 \cite{cvejic_wavelet_2002}).
@@
 We repeat this step as long as such a swap is still possible.
-Though this is not guaranteed to yield an optimal TSP tour, it does produce tours which are simple; that is, every crossing is removed.% (Figure~\ref{fig:TwoOpt}).
+Though this is not guaranteed to yield an optimal TSP tour, it does produce aesthetically pleasing tours which are simple; that is, every crossing is removed.% (Figure~\ref{fig:TwoOpt}).
 
@@
 \subsubsection{The choice of non-overlapping windows}
-Though some other works use transforms with overlapping windows \cite{hwan_sik_yun_acoustic_2010,geleta_pixinwav_2021}, changing different STFT bins independently leads to STFTs that do not correspond to any real signal due to discrepancies between overlapping windows.
+Though some other works use transforms with overlapping windows \cite{yun2009acoustic,geleta_pixinwav_2021}, changing different STFT bins independently leads to STFTs that do not correspond to any real signal due to discrepancies between overlapping windows.
 An algorithm like Griffin-Lim \cite{griffin1984signal} can recover a signal whose spectrogram has a locally minimal distance to the perturbed STFT, but we find that this step introduces an unacceptable level of distortion both in the target and the carrier audio.
@@
 Beyond shifting and scaling the targets coordinates vertically, we may also need to re-parameterize them in time, since, in general, the SWS-STFT sequence will not have the same number of samples as the shifted target $\hat{T}$.
-Furthermore, the target curves are cyclic, so the starting point is arbitrary, nor does it matter if we traverse the curve left or right.
+Furthermore, the target curves are cyclic, so the starting point is arbitrary, nor does it matter if we traverse the curve left or right, or at a constant speed.
 This gives us a lot of freedom in how we choose to re-parameterize the target to best match the signal even before we perturb the signal.
@@
 Likewise, for the mesh segmentation dataset, we hide each Hamiltonian path in three different audio clips from the Tzanetakis dataset.
-In all cases, we encode the audio using lossy mp3 compression at 64 kbps.
+In all cases, we use an STFT window length of 1024 at a sample rate of 44100hz, and we encode the audio using lossy mp3 compression at 64 kbps.
 
@@
 We also see a positive effect of the Viterbi alignment from Section~\ref{sec:reparam} on the SNR in Figure~\ref{fig:ResultsViterbiExperiment}.
+Though $\approx$+1dB may not seem significant, it can make a huge difference in audio, particularly in quiet regions.
 Finally, we run an experiment on the Caltech-101 dataset by choosing 4 random frame offsets per embedding, and we see in Figure~\ref{fig:ShiftsExperiment} that the algorithm of Section~\ref{sec:framealignments} recovers alignments well.
@@
 
-Though the experiments above are encouraging, SNR can be misleading; frequencies that are more audible may actually have a higher SNR.
+Though the experiments above are encouraging, SNR can be misleading; frequencies that are more audible may actually have a higher SNR due to psychoacoustic phenomena.
 To address this, we performed a crowd-sourced listening experiment on the Amazon Mechanical Turk where we embedded a random image from the Caltech-101 dataset in each of the Tzanetakis clips.
@@
 
-\section{Discussion / Conclusion}
+\section{Discussion / Supplementary Material}
 
@@
 Decoding is nearly instantaneous, as it only requires computing the STFT of a few frequencies.
+
+To show off our pipeline, we created an interactive viewer in Javascript using WebGL that can load in and decode any mp3 file.
+The viewer plays the decoded curve synchronized to the music.
+We also provide a variety of 2D and 3D examples.
+To view our source code for encoding and decoding and look at these examples, please visit \url{https://curvesteg.s3.amazonaws.com/index.html}
 

### 2023-01-29 writeup/paper.tex
A few initial updates

@@
 %
-\author{First Author\inst{1}\orcidID{0000-1111-2222-3333}}
+\author{Christopher J Tralie\inst{1}\orcidID{0000-0003-4206-1963}}
 %
-\authorrunning{F. Author et al.}
+\authorrunning{C. Tralie}
 % First names are abbreviated in the running head.
@@
 %
-\institute{Princeton University, Princeton NJ 08544, USA 
-\email{lncs@springer.com}}
+\institute{Ursinus College, Collegeville PA 19426, USA 
+\email{ctralie@alumni.princeton.edu}}
 %
@@
 Our embedding scheme is designed to faithfully preserve the geometry of these loops after lossy compression, while keeping their presence undetectable to the audio listener.
-To accomplish this, we hide each dimension of the curve in a different frequency, and we perturb a regularized version of the magnitude of that frequency to best match the target curve at that dimension, while hiding scale information in that frequency's phase.
+To accomplish this, we hide each dimension of the curve in a different frequency, and we perturb a sliding window sum of the magnitude of that frequency to best match the target curve at that dimension, while hiding scale information in that frequency's phase.
 In the process, we exploit geometric properties of the curves to help to more effectively hide and recover them.
@@
 The viewer plays the decoded curve synchronized to the music.
-We also provide a variety of 2D and 3D examples.
+We provide a variety of 2D and 3D precomputed examples to demonstrate our capabilities.
 To view our source code for encoding and decoding and look at these examples, please visit \url{https://curvesteg.s3.amazonaws.com/index.html}
+
+%\footnote{Decoding is so quick that $\lambda$, $\ell$, and shift can be varied at interactive rates}
 

### 2023-01-29 writeup/paper.tex
Proofreading paper

@@
 Steganography is the process of hiding one data stream ``in plain sight'' within another data stream known as a ``carrier.''  In this work, we are interested in using audio as a carrier to store images, which has been relatively unexplored in the academic literature (Section~\ref{sec:priorwork}).
-As with any stegonographic technique, people can use this as a general means of covert communication, but it can also be used for artists to hide images and to watermark their tunes.
+As with any stegonographic technique, one can use this as a general means of covert communication, artists can also use it to hide images and to watermark their tunes.
 One such example occurred when Aphex Twin embedded a face image inside the spectrogram of their ``Windowlicker'' song \cite{mathews2004music}, though the technique yields very loud, inharmonic, scratchy sounds.
@@
 
-To make our audio steganography system as robust and usable as possible, we have the following design goals:
+To make our audio steganography system as robust and as usable as possible, we have the following design goals:
 \begin{enumerate}
@@
 Following the authors of \cite{kaplan2005tsp}, we use Secord's technique for Voronoi stippling \cite{secord2002weighted}, which takes an initial sample of points according to some density weights $W$ and then repeatedly moves them closer the weighted centroid of their Voronoi regions (an instance of Lloyd's algorithm) so that they are spread more evenly.
-Secord \cite{secord2002weighted} takes the weight $W_{ij}$ at a pixel to be inversely proportional to its brightness, using a weight of $0$ above some brigtness threshold $b$.
+Secord \cite{secord2002weighted} takes the weight $W_{ij}$ at a pixel to be inversely proportional to its brightness, using a weight of $0$ above some brightness threshold $b$.
 This leads more dots to concentrate in darker regions; however, the algorithm may fail to sample any dots along important edges between brighter regions (the authors of \cite{li2011structure} also observed this).
@@
 In practice, we use the Blossom-5 algorithm \cite{kolmogorov2009blossom} to find perfect matches of the dual graph.
-Then, adding edges between unpaired triangles leads to a set of disconnected cycles (third column of Figure~\ref{fig:HamiltonianHorse}), which are connected by a spanning set of edges between paired triangles.
+Then, adding edges between unpaired triangles leads to a set of disconnected cycles (third column of Figure~\ref{fig:HamiltonianHorse}), which one can connect by a spanning set of edges between paired triangles.
 Finally, the spanning edges are split into bridges between the disconnected cycles, joining them together into one large cycle that covers the surface of the triangle mesh.
@@
 We now formulate an objective function that trades off Equation~\ref{eq:stegsnr} and Equation~\ref{eq:distortion}.
-Let $T = (T_1, T_2, \hdots, T_N \}$ be the sequence of points of the target curve to hide, where each $T_i \in \mathbb{R}^d$, and let $T_{i, m}$ refer to $m^{\text{th}}$ coordinate of $T_i$, and let $x$ be a set of audio samples which will serve as a carrier.
+Let $T = (T_1, T_2, \hdots, T_N )$ be the sequence of points of the target curve to hide, where each $T_i \in \mathbb{R}^d$, and let $T_{i, m}$ refer to $m^{\text{th}}$ coordinate of $T_i$, and let $x$ be a set of audio samples which will serve as a carrier.
 The goal is to perturb the samples of $x$ so that some function of $x$ matches $T$ as closely as possible.
@@
 and we factor $S$ it into its magnitude and phase components $M$ and $P$, respectively.
-Next, we choose a subset of $d$ frequencies $k_i$, each of which will hide a different dimension of $T$.
+Next, we choose a subset of $d$ frequencies $k_i, i \in \{1, 2, \hdots, d\}$, each of which will hide a different dimension of $T$.
 Given a second window length $\ell$, we then define the following {\em sliding window sum} function, which we apply to each row $k_i$ of the magnitudes of $S$ that we wish to perturb to obtain the SWS-STFT
@@
 In other words, we want the magnitude SW-STFT of a perturbed signal to match the target coordinate as well as possible (minimizing Equation~\ref{eq:distortion}), while preserving the original audio as well as possible (minimizing Equation~\ref{eq:viterbiobj}), according to $\lambda$.
-A greater $\lambda$ means that the signal will fit the original audio better, at the cost of a noisier curve.
+A greater $\lambda$ means that the signal $\hat{M}$ will fit the original audio better, at the cost of a noisier curve.
 Figure~\ref{fig:LambdaEffect} shows an example.
 
-After solving for $\hat{M_{k_i, j}}$, we replace all rows of $M_{k_i}$ with $\hat{M_{k_i}}$, and we perform an inverse STFT of $M e^{i P}$ for the original phases $P$ (Section~\ref{sec:componentscales} will explain when it is necessary to modify the phases as well).
-We then save the resulting audio in a compressed format, and recover the hidden signal by loading it in and extracting the corresponding components of the magnitude SW-STFT.
+After solving for $\hat{M_{k_i, j}}$, we replace all rows of $M_{k_i}$ with $\hat{M_{k_i}}$, and we perform an inverse STFT of $M e^{i P}$ using the original phases $P$ (Section~\ref{sec:componentscales} will explain when it is necessary to modify the phases as well).
+We then save the resulting audio in a compressed format, and we recover the hidden signal by loading it and extracting the corresponding components of the magnitude SW-STFT.
 
@@
 
-Overall, we see slightly higher distortions and lower SNRs for 3D embeddings than 2D embeddings, which makes sense since there is one additional coordinate to hide.
+Overall, we see slightly higher distortions and lower SNRs for 3D embeddings than 2D embeddings, which makes sense since there is one additional coordinate to hide in 3D.
 As expected, increasing $\lambda$ increases both the SNR and distortion, as shown in Figure~\ref{fig:ResultsFixedWin}.
@@
 To address this, we performed a crowd-sourced listening experiment on the Amazon Mechanical Turk where we embedded a random image from the Caltech-101 dataset in each of the Tzanetakis clips.
-We split them into 4 groups with no embedding (control), and with $\lambda = 0.1, 1, 10$, and we asked the listeners to rate the quality of the noise on the 5 point impairment scale of \cite{bassia2001robust} (5: imperceptible, 4: perceptible but not annoying, 3: slightly annoying, 2: annoying, 1: very annoying).
+We split them into 4 groups with no embedding (control), and with $\lambda = 0.1, 1, 10$.
+We asked the listeners to rate the quality of the noise on the 5 point impairment scale of \cite{bassia2001robust} (5: imperceptible, 4: perceptible but not annoying, 3: slightly annoying, 2: annoying, 1: very annoying).
 In our experiment, we had 46 unique Turkers, 21 of whom participated in at least 40 rankings.
 Figure~\ref{fig:TurkResults} shows the results.
-Mean opinion scores (MOS) are correlated with $\lambda$, but there's not much of a difference between $\lambda=0.1$ and $\lambda=1$, which suggests using the former as a rule of thumb due to its lower geometric distortion.
+Mean opinion scores (MOS) are correlated with $\lambda$, but there is little difference between $\lambda=0.1$ and $\lambda=1$, which suggests using the former as a rule of thumb due to its lower geometric distortion.
 % We see a Pearson correlation of $r=0.48$ between the mean opinion score and the SNR in dB.
@@
 We provide a variety of 2D and 3D precomputed examples to demonstrate our capabilities.
-To view our source code for encoding and decoding and look at these examples, please visit \url{https://curvesteg.s3.amazonaws.com/index.html}
+To view our supplementary material, source code for encoding and decoding, and live examples, please visit \url{https://github.com/ctralie/AudioCurveSteganography}
 
